\book{尼雅的儿子巴录的启示录，或巴录二书}

\textbf{Announcement} of the coming Destruction of Jerusalem to Baruch
\par
\textbf{向巴录宣布耶路撒冷即将被毁的消息}
\par

\Chapter

\Verse And it came to pass in the twenty-fifth year of Jeconiah, king of Judah, that the word of the \LORD came to Baruch, the son of Neriah, and said to him: 犹大王耶哥尼雅\footnote{耶哥尼雅（Jeconiah）即哥尼雅、约雅斤（Jehoiachin），是法老所立的王，为法老征税。
参王下二三34～35。
}二十五年，耶和华的话语传到尼雅的儿子巴录那里，对他说：
\Verse 'Have you seen all that this people are doing to Me, that the evils which these two tribes which remained have done are greater than (those of) the ten tribes which were carried away captive 
'你可曾看见这百姓对我所行的一切，这两个支派所行的恶，比被掳走的十个支派所行的恶还大。
\Verse For the former tribes were forced by their kings to commit sin, but these two of themselves have been forcing and compelling their kings to commit sin. 
因为以前的诸支派是被他们的国王们逼迫的，而这犹大、便雅悯的民\footnote{
these two of themselves. 犹大国主要是犹大、便雅悯两支派。
}却一直在逼迫和蛊惑他们的国王们犯罪。
\Verse For this reason, behold I bring evil upon this city, and upon its inhabitants, and it shall be removed from before Me for a time, and I will scatter this people among the Gentiles that they may do good to the Gentiles. And My people shall be chastened, and the time shall come when they will seek for the prosperity of their times. 
因为这个原因，看哪，我将罪恶降临在这城和城中的居民身上，使这城和城中的居民，
在我面前被移走一段时间，我要把这百姓分散在外邦人中间，叫他们向外邦人行善。
我的子民必受责罚，到了他们要寻求时代的繁荣的时候。

\Chapter
\Verse For I have said these things to you that you may bid Jeremiah, and all those that are like you, to retire from this city.
我对你们说这些话，是要叫你们叫耶利米和所有像你们一样的人，从这城中退去。

\Verse For your works are to this city as a firm pillar,
And your prayers as a strong wall.'
因为你们的工作对这城来说，就像坚固的柱子一样。
你的祷告如坚固的墙。'

\Chapter 
\Verse And I said: 'O \LORD, my \LORD, have I come into the world for this purpose that I might see the evils of my mother Not (so) my Lord. 
我说：'耶和华啊，我的主啊，我来到世界上，就是为了这个目的，好让我看见我母亲的罪恶，而不是（如此）我的主。
\Verse If I have found grace in Your sight, first take my spirit that I may go to my fathers and not behold the destruction of my mother. 
我若在你的眼中找到了恩典，就先取我的灵，使我可以到我的祖宗那里去，不要让我看到我母亲的毁灭。
\Verse For two things vehemently constrain me: for I cannot resist you, and my soul, moreover, cannot behold the evils of my mother. 
因为有这两件事使我完全地受制于你：一因为我不能抗拒你，
二且我的灵魂也不能看我母亲的罪恶。
\Verse But one thing I will say in Your presence, O \LORD. 
但有一件事我要在你面前说，主啊，我要在你面前说，
\Verse What, therefore, will there be after these things for if you destroy Your city, and deliver up Your land to those that hate us, how shall the name of Israel be again remembered 
你若毁坏了你的城，把你的地交到那恨我们的人手中，以色列的名将如何再被人记起，
\Verse Or how shall one speak of Your praises or to whom shall that which is in Your law be explained Or shall the world return to its nature of aforetime), and the age revert to primeval silence And shall the multitude of souls be taken away, and the nature of man not again be named And where is all that which you did say regarding us'   
你的名将如何说起你的赞美，你的律法中的事将如何向谁解释，世界将恢复到从前的本性，时代将恢复到原始的寂静，众人的灵魂将被夺去，人的本性将不再被人称颂，你对我们所说的一切话将在哪里？

\Chapter
\Verse And the \LORD said unto me: 'This city shall be delivered up for a time,
 And the people shall be chastened during a time,
 And the world will not be given over to oblivion.
耶和华对我说：'这城必被交出来，直到永远。
'这城必被交出一段时间。民众也要在一段时期内受到责罚。世人也不至于被遗忘。
\par
\textbf{4:2-7 天上的耶路撒冷}
\par
\Verse [Dost you think that this is that city of which I said: "On the palms of My hands have I graven you" 
你们以为这就是我说的那城吗？"我在我的手掌上刻下了你的名字" 
\Verse This building now built in your midst is not that which is revealed with Me, that which prepared beforehand here from the time when I took counsel to make Paradise, and showed Adam before he sinned, but when he transgressed the commandment it was removed from him, as also Paradise. 
现在建在你们中间的这建筑，不是我与你们中间的那座城，不是我与你们中间的那座城，而是我在亚当犯罪之前，从我出谋划策，制造天堂的时候，就在这里预先预备好的，在亚当犯罪之前，就把它从他身上移走了，也是天堂。
\Verse And after these things I showed it to My servant Abraham by night among the portions of the victims. 
在这事之后，我就在夜里在众人中把它给我的仆人亚伯拉罕看了。
\Verse And again also I showed it to Moses on Mount Sinai when I showed to the likeness of the tabernacle and all its vessels. 
我又在西奈山上向摩西显露了它，当我把帐幕和所有的器皿都显露出来。
\Verse And now, behold, it is preserved with Me, as Paradise. 
 现在，看哪，它与我同存，如同乐园一样。
\Verse Go, therefore, and do as I command you.']
所以你们要去，照我所吩咐的去行。]

\Chapter
\textbf{Baruch's Complaint and God's Reassurance}
\textbf{巴录的抱怨和上帝的保证}
\par
\Verse And I answered and said:
我回答说：“

'So then I am destined to grieve for Zion,
所以，我注定要为锡安忧伤。

For your enemies will come to this place and pollute Your sanctuary,
因为你的敌人会来到这里，污染你的圣地。

And lead your inheritance into captivity,
并把你的遗产引向囚途。

And make themselves masters of those whom you have loved,
并让自己成为你所爱的人的主人。

And they will depart again to the place of their idols,
他们将再次离开，回到他们偶像的地方。

And will boast before them:
并将在他们面前夸耀

And what will you do for Your great name'
你要为你的圣名做什么”

\Verse And the \LORD said unto me:
主对我说：“

        'My name and My glory are unto all eternity;
我的名和我的荣耀，直到永远。

        And My judgment shall maintain its right in its own time.
我的审判，必在自己的时间里保持它的权利。

\Verse And you shall see with your eyes
你们要用你们的眼睛看见

        That the enemy will not overthrow Zion,
敌人不会推翻锡安。

        Nor shall they burn Jerusalem,
他们也不得烧毁耶路撒冷。

        But be the ministers of the Judge for the time.
但你们要作审判者的臣子。

\Verse But do you go and do whatsoever I have said unto you.
但你们要去行我所吩咐你们的事。

\Verse And I went and took Jeremiah, and Adu, and Seriah, and Jabish, and Gedaliah, and all the honorable men of the people, and I led them to the valley of Kidron, and I narrated to them all that had been said to me. 
我就带着耶利米、亚都、西利亚、耶利米、雅比、吉大利和百姓中所有尊贵的人，我就带着他们到基隆谷去，把所讲的一切话，都告诉他们。
\Verse And they lifted up their voice, and they all wept. 
他们就高声呼喊，都哭了起来。
\Verse  And we sat there and fasted until the evening.
我们就坐在那里禁食，直到傍晚。

\par
6—8. Invasion of the Chaldeans and their Entrance into the City after the Sacred Vessels were hidden and the City's Walls overthrown by Angels
\par
迦勒底人的入侵和他们在圣器被藏起来，城墙被天使推倒后进入城中。
\par
\Chapter
\Verse And it came to pass on the morrow that, lo! the army of the Chaldees surrounded the city, and at the time of the evening, I, Baruch, left the people, and I went forth and stood by the oak. 
到了那日，迦勒底人的军队包围了这城，傍晚时，我巴录离开百姓，出去站在橡树旁。
\Verse And I was grieving over Zion, and lamenting over the captivity which had come upon the people.
我为锡安忧愁，为百姓被掳的事哀叹。
\Verse And lo! suddenly a strong spirit raised me, and bore me aloft over the wall of Jerusalem. 
忽然有一个强壮的灵把我抬起来，把我高高举过耶路撒冷的城墙。
\Verse And I beheld, and lo! four angels standing at the four corners of the city, each of them holding a torch of fire in his hands. 
我看见，有四位天使站在城的四角，各拿着火把。
\Verse And another angel began to descend from heaven. and said unto them: 'Hold your lamps, and do not light them till I tell you. 
又有一个天使从天上降下，对他们说：'你们要拿着灯，不要拿着火把。'你们拿着灯，在我不告诉你们之前，不要点灯。
\Verse For I am first sent to speak a word to the earth, and to place in it what the \LORD the Most High has commanded me.' 
因为我先是被差遣到地上说一句话，把至高的主所吩咐我的事，放在地上。
\Verse And I saw him descend into the Holy of Holies, and take from there the veil, and holy ark, and the mercy-seat, and the two tables, and the holy raiment of the priests, and the altar of incense, and the forty-eight precious stones, wherewith the priest was adorned and all the holy vessels of the tabernacle. 
我看见他下到圣所里，从那里取了面纱、圣舟、慈悲座、两张桌子、祭司的圣衣、香坛、四十八块宝石、祭司所穿的四十八块宝石和会幕里所有的圣器。
\Verse  And he spoke to the earth with a loud voice:
他用高声对着地说话：“

        'Earth, earth, earth, hear the word of the mighty God,
地啊，地啊，地啊，地啊，地啊，你要听大能的\神 的话。

        And receive what I commit to you,
并接受我对你的承诺。

        And guard them until the last times,
并守护他们，直到最后的时候。

        So that, when you are ordered, you may restore them,
这样，当你被命令时，你可以恢复它们。

        So that strangers may not get possession of them.
好叫外人不能占有他们。

\Verse For the time comes when Jerusalem also will be delivered for a time,
这时候到了，耶路撒冷也要被交付一段时间。

        Until it is said, that it is again restored for ever.'
直到有话语说：它再次恢复了，并将矗立直到永远。”

\Verse And the earth opened its mouth and swallowed them up.
大地张开嘴，把他们吞没了。

\Chapter 
\Verse  And after these things I heard that angel saying unto those angels who held the lamps: 'Destroy, therefore, and overthrow its wall to its foundations, lest the enemy should boast and say:
这事之后，我听见那天使对那些拿着灯的天使说：“你们要毁坏它，把它的墙推倒，推倒它的根基，免得敌人夸口说：

        " We have overthrown the wall of Zion,
‘我们推翻了锡安城的城墙。

        And we have burnt the place of the mighty God."'
		我们烧毁了大能的\神 的地方。’”

\Verse        And they have seized the place where I had been standing before.
他们又夺取了我以前所站的地方。

\Chapter
\Verse Now the angels did as he had commanded them, and when they had broken up the corners of the walls, a voice was heard from the interior of the temple, after the wall had fall saying:
天使们照他所吩咐的去行，当他们把墙角拆开，墙倒了之后，有声音从殿内传来，说：

\Verse        'Enter, you enemies,
‘你们这些仇敌，进去吧。

        And come, you adversaries;
你们这些悖逆，进来吧。

        For he who kept the house has forsaken (it).'
		因为那守着房子的人已经抛弃了它。’

\Verse And I, Baruch, departed. 
我巴录就离开了。
\Verse And it came to pass after these things that the army of the Chaldees entered and seized the house, and all that was around it. 
And they led the people away captive and slew some of them, and bound Zedekiah the king, and sent him to the king of Babylon.
这事之后，迦勒底人的军队就进屋里，夺取了房子和周围的一切。
他们掳走百姓、杀了一些人，把王西底家捆绑起来、把他送去见巴比伦王。
\par
9—12. \textbf{First Fast of seven Days}: Baruch to remain amid the Ruins of Jerusalem and Jeremiah to accompany the Exiles to Babylon. Baruch's Dirge over Jerusalem
\par
\textbf{第一次禁食七天}。
巴录要留在耶路撒冷的废墟中，耶利米要陪同流亡者去巴比伦。巴录哀耶路撒冷
\par
\Chapter
\Verse And I, Baruch, came, and Jeremiah, whose heart was found pure from sins, who had not been captured in the seizure of the City. 
我巴录，耶利米也来了，他的心是洁净的，没有在围城时被俘虏。
\Verse And we rent our garments, we wept, and mourned, and fasted seven days.
我们就脱了衣裳，哀哭、忧伤，我们禁食了七天。
\Chapter
\Verse And it came to pass after seven days, that the word of God came to me, and said unto me: 
七天的禁食后，\神 的话语传来，对我说：
\Verse 'Tell Jeremiah to go and support the captivity of the people unto Babylon. 
“叫耶利米去帮被掳的百姓到巴比伦去。
\Verse But do you remain here amid the desolation of Zion, and I will show to you after these days 'what will befall at the end of days.' And I said to Jeremiah as the \LORD commanded me. 
但你要在锡安的荒凉中留在这里，过了这些日子，
我必向你表明，'末世的事，必有什么结果'。
我照着主的吩咐对他说了。
\Verse And he, indeed, departed with the people, but I, Baruch, returned and sat before the gates of the temple,
他就和众人一起离开了，我巴录却回来坐在圣殿的门前，为锡安的事哀叹。
\Verse and I lamented with the following lamentation over Zion and said:
我对锡安哀叹着说：
\par
\Verse  'Blessed is he who was not born,
'没有出生的人有福了。

      Or he, who having been born, has died.
或者说，他生下来，就死了。

\Verse    But as for us who live, woe unto us,
至于我们活着的人，则有祸了。

      Because we see the afflictions of Zion,
  因为我们看到了锡安的苦难。

      And what has befallen Jerusalem.
还有耶路撒冷所遭遇的事。

\Verse    I will call the Sirens from the sea,
我将从海上召唤海妖，

      And you Lilin, come you from the desert,
从沙漠中召唤夜魔，

      And you Shedim and dragons from the forests:
从丛林中召唤出鬼魔\footnote{
Shedim，曾出现在诗篇106:37、申命记32:17。和合本翻译为鬼魔。
是一种索要小童和动物祭品的鬼怪，可恶可善。
在希伯来文翻译到希腊文中，受琐罗亚斯德教二元善恶论的影响，
Shedim被翻译成Daimonia。
但希伯来和伊斯兰文化中，Shedim仍具有两面性。
}和巨龙

      Awake and gird up your loins unto mourning,
醒来，在哀伤中束起你们的腰带。

      And take up with me the dirges,
	  和我一起拿起那首曲子

      And make lamentation with me.
	  与我一同吟唱这首哀歌。

\Verse    Ye husbandmen, sow not again;
丈夫们，你们不要再播种了。

      And, O earth, wherefore give you your harvest fruits
	  地啊，你的庄稼的果子，为什么要赐给你呢？

      Keep within you the sweets of your sustenance.
	  你要把你的日用饮食放在自己之中。

\Verse  And thou, vine, why further do you give your wine;
葡萄树啊，你何必再献上你的酒。

      For an offering will not again be made from there in Zion,
因为在锡安，你的祭品不会再从那里献上了。

      Nor will first-fruits again be offered.
	  连你的初果也不会再被献上。

\Verse     And do ye, O heavens, 'withhold your dew,
我的天啊，你们要把你们的露水扣住。

        And open not the treasuries of rain:
		不要打开雨水的宝库。

\Verse     And do thou, O sun withhold the light of your rays.
太阳啊，你要隐瞒你的光芒。

        And do thou, O moon, extinguish the multitude of your light;
		月亮啊，你也要熄灭你的光芒。

        For why should light rise again
		光又为什么要复活呢？

        Where the light of Zion is darkened
		锡安之光已被黑暗吞噬。

\Verse     And you, you bridegrooms, enter not in,
你们这些新郎新娘，不要进去。

        And let not the brides adorn themselves with garlands;
		不要让新娘们用花环装饰自己。

        And, you women, pray not that you may bear.
妇人啊，不要祈求你们将孕生孩子。

\Verse    For the barren shall above all rejoice,
因为贫瘠的人，必有喜乐。

        And those who have no sons shall be glad,
		没有儿子的人将会高兴。

        And those who have sons shall have anguish.
有儿子的人，必有苦难。

\Verse     For why should they bear in pain,
因为为何（你要）他们要忍受痛苦

        Only to bury in grief
		又只能埋葬在悲伤之中。

\Verse     Or why, again, should mankind have sons
或又问，人为何要生诸子？

        Or why should the seed of their kind again be named,
		又为何为他们起了名字？

        Where this mother is desolate,
		这母亲已荒弃了，

        And her sons are led into captivity
		诸子将被囚俘

\Verse     From this time forward speak not of beauty,
从现在起，不要说美了

        And discourse not of gracefulness.
		也不要说什么恩典的话。

\Verse     Moreover, you priests take you the keys of the sanctuary,
更甚，你们这些祭司拿着圣所的钥匙。

        And cast them into the height of heaven,
		并把他们扔到天上的高处。

        And give them to the \LORD and say:
		把他们交给主，说：

        "Guard Your house Thyself,
		"你要亲自看守你的房子。

        For lo! we are found false stewards."
		因为我们被发现是假管家。"

\Verse     And you, you virgins; who weave fine linen
你们这些处男、处女，织得好亚麻布、

        And silk with gold of Ophir,
		在绸缎上镶嵌了俄斐\footnote{
		俄斐（Ophir），富饶的商港。
		列王纪上10中记载所罗门王得到希兰王自俄斐派船送来黄金、檀香木和宝石。
		}的金子的人们。

        Take with haste all (these) things
		你们当匆匆忙忙地拿着这些东西

        And cast (them) into the fire,
		并把（他们）扔进火里。

        That it may bear them to Him who made them,
		让它将它们归于创造它们的主。

        And the flame send them to Him who created them,
		而火焰将它们送去给创造它们的\神 。

        Lest the enemy get possession of them.'
		免得仇敌占了他们。’

\Chapter
\Verse Moreover, I, Baruch, say this against you, Babylon:
我，我巴录，对你，巴比伦，直面说：

        'If you had prospered,
'如果你有了繁荣，

        And Zion had dwelt in her glory,
而锡安只得住在她的往昔的荣耀中。

        Yet the grief to us had been great
我们的悲痛将是巨大的：

        That you should be equal to Zion.
你何德何能得以与锡安同座。

\Verse       But now, lo! the grief is infinite,
呜呼！但现在，悲痛是无限的，

        And the lamentation measureless,
哀叹是无量的。

        For lo! you are prospered
		因为，你已经得到了丰厚的财富

        And Zion desolate.
		而锡安荒凉颓败。

\Verse       Who will be judge regarding these things
谁来审判这些事呢？

        Or to whom shall we complain regarding that which has befallen us
		或者说，我们该向谁抱怨我们所遭遇的一切？

        O Lord, how have you borne (it)
		主啊，你如何承担我们的抱怨？

\Verse       Our fathers went to rest without grief,
我们的父辈们安息了，却没有大悲恸，

        And lo! the righteous sleep in the earth in tranquility;
呜呼！义人安详地睡在地上。

\Verse       For they knew not this anguish,
因为他们不知道这等苦难

        Nor yet had they heard of that which had befallen us.
		因为他们不曾听说过我们所遭遇的事。

\Verse       Would that you had ears, O earth,
愿你有耳朵，大地。

        And that you had a heart, O dust:
愿你有一颗心，尘埃。

        That you might go and announce in Sheol,
		你可以去在阴间\footnote{
	原文Sheol，是亡魂所去的黑暗之地。
	参民数记16:33等章节。
	}宣布。

        And say to the dead:
与那些死去的人说：

\Verse       "Blessed are you more than we who live."'
“你们比我们活着的人更有福气”。

\Chapter
\Verse But I will say this as I think.
但我要照我所想的那样说。

And I will speak against you, O land, which alt prospering
我要反对\footnote{Speak against. }你们这块繁荣的土地！

\Verse The noonday does not always burn.
正午的太阳并会永远燃烧。

Nor do the rays of the sun constantly give light.
太阳的光芒也总有一日将熄灭。

\Verse Do not expect Land hope that you will always he prosperous and rejoicing.
不要指望你的地永远都是兴高采烈，喜气洋洋。

And be not greatly up lifted and boastful.
或高高在上、浮夸哗众。

\Verse For assuredly in its own season shall the (divine) wrath awake against you.
你要晓得，在你之季，\神 的愤怒必临于你。

Which now in long-suffering is held in as it were by reins.
长久的苦难将临、如同缰绳束马。

\par
12:5—13. Second Fast. Revelation as to the coming judgment on the Heathen.
\par
12:5—13. 第二次禁食。关于异教徒即将受到审判的启示。
\par

\Verse And when I had said these things, I fasted seven days.

\Chapter
\Verse And it came to pass after these things, that I, Baruch, was standing upon Mount Zion, and lo! a voice came from the height and said unto me: 
在这些事情之后，我，巴录，站在锡安山上。
一个声音从高处传来，对我说：
\Verse 'Stand upon your feet, Baruch, and hear the word of the mighty God.'
“站好了，巴录，聆听大能的\神 的话语。”

\Verse Because you have been astonished at what has befallen Zion, you shall therefore be assuredly preserved to the consummation of the times, that you may be for a testimony. 
因为你们对锡安的遭遇感到惊奇，所以你们必被保全，直到时代的终结，为你们作见证。
\Verse So that, if ever those prosperous cities say: 
这样，那些繁华的城池，若说：
\Verse 'Why hath the mighty God brought upon us this retribution' Say you to them, you and those like you who shall have seen this evil: '(This is the evil) and retribution which is coming upon you and upon your people in its (destined) time that the nations may be thoroughly smitten. 
“大能的神为什么要把这报应降临在我们身上？”
你对他们说：“你们和你们这样的人，你们要看到这恶：‘（这是恶）和报应，在它（注定的）时间里，你们和你们的子民将被彻底地击倒。’”

\Verse And then they shall be in anguish. 
那时，他们必受苦难。
\Verse And if they say at that time:
到了那时候，他们若说：

\Verse For how long you will say to them:

        "Ye who have drunk the strained wine,
		喝了精酿的滤酒的人，

        Drink you also of its dregs,
		也要把酒里曾滤去的渣滓也喝了，

        The judgment of the Lofty One
		崇高者的判决

        Who has no respect of persons."'
		并不尊重人们。”

\Verse       On this account he had aforetime no mercy on His own sons,
因此，他以前对自己的儿子们毫不怜悯。

        But afflicted them as His enemies, because they sinned,
		但却把他们当作敌人来折磨，因为他们犯了罪。

\Verse     Then therefore were they chastened
因此，他们被责罚了

        That they might be sanctified.
		以此，他们才得以被洁净。

\Verse But now, you peoples and nations, you are guilty
但现在，你们这些诸支派和诸国，你们是有罪的。

         Because you have always trodden down the earth,
		 因为你们走过世间，

         And used the creation unrighteously.
		 并不义地使用了造物。
		 
\Verse For I have always benefited you.
 因我一直以来都给你们带来了好处。

        And you have always been ungrateful for the beneficence.
		而你却总是不领情，对我的恩惠不领情。

\par
14—19. The Righteousness of the Righteous has profited neither them nor their City; God's Judgments are incomprehensible; the World was made for the Righteous, yet they pass and the World remains (14). Answer—Man knows God's Judgments and has sinned willingly. This World is a Weariness to the Righteous but the next is theirs (15), to be won through Character whether a Man's Time here be long or short (16—17). Final Weal or Woe—the supreme Question (18—19).
\par
14—19. 义人的义，既没有得到他们的利益，也没有得到他们的城的利益；
神的审判是无法理解的；世界是为义人而造的，然而他们过去了，世界还在（14）。答人知道神的审判，心甘情愿地犯罪。
这个世界对义人来说是一种疲惫，但下一个世界是他们的(15)，无论人在这里的时间是长是短，都要靠品格来赢得(16-17)。最后的幸福还是邪恶----最高的问题(18-19)。
\par
\Chapter 
\Verse And I answered and said: 'Lo! you have shown me the method of the times, and that which shall be after these things, and you have said unto me, that the retribution, which has been spoken of by you, shall come upon the nations. 
我回答说：'你们已经向我指明了时代的方法，和这些事以后的事，又对我说，你们所说的报应，必临到万国。

\Verse And now I know that those who have sinned are many, and they have lived in prosperity,' and departed from the world, but the few nations will be left in those times, to whom those words shall he said which you did say. 
现在我知道，犯了罪的人多了，住在富足的地方，离开了世界，到了那时候，只剩下那少数的国家，就是你所说的那些话，要留给他们。
\Verse For what advantage is there in this, or what (evil), worse than what' we have seen befall us, are we to expect to see
这有什么好处呢，或者有什么比我们所看见的更坏的（恶事），我们还能指望看见吗？
\par
\Verse But again I will speak in Your presence: 
但我又要在你面前说话
\Verse What have they profited who had knowledge before you and have not walked in vanity as the rest of the nations, and have not said to the dead: "Give us life," but always feared you, and have not left Your ways 
在你面前有知识的人，不像其余的民族那样虚荣地行走，不对死人说："给我们生命，却一直敬畏你，不离开你的道路。
\Verse And lo! they have been carried off, nor on their account have you had mercy on Zion. 
别人若作恶，是因锡安
\Verse And if others did evil, it was due to Zion that on account of the works of those who wrought good works she should be forgiven, and should not be overwhelmed on account of the works of those who wrought unrighteousness. 
因行善的人行善的事，就该得赦免，不因行不义的人的事，就该被压倒。
\Verse But who, O \LORD, my \LORD, will comprehend Your judgment,
耶和华啊，我的主啊，谁能明白你的审判呢。

        Or who will search out the profoundness of Your way
        又谁会寻得你的道之深刻？

        Or who will think out the weight of Your path
        又谁会懂得你的道之重要？

\Verse Or who will be able to think out Your incomprehensible counsel
又谁会懂得你的神秘

        Or who of those that are born has ever found
又在世间曾走过的人有几个懂得

        The beginning or end of Your wisdom
你智慧的始终

\Verse For we have all been made like a breath. 
因为我们都是在呼吸的气息中被造出来的。
\Verse  For as the breath ascends involuntarily, and again dies, so it is with the nature of men, who depart not according to their own will, and know not what will befall them in the end. 
人的本性也是如此，不按自己的意思离开，也不知道终究会有什么结果。
\Verse For the righteous justly hope for the end, and without fear depart from this habitation, because they have with you a store of works preserved in treasuries. 
正义的人，因着公义的人盼望着末日，就不惧怕离开这住处，因为他们有存留在库房里的工分。
\Verse On this account also these without fear leave this world, and trusting with joy they hope to receive the world which you have promised them. 
他们也因此离开这世界，无所畏惧，就满心欢喜地信靠你，盼望得到你所应许的世界。
\Verse But as for us—woe to us, who also are now shamefully entreated, and at that time look forward (only) to evils. 
至于我们，我们也是可耻的，现在也是可耻的，在那时候，只顾着往前看（只顾着）罪恶。
\Verse But you know accurately what you have done by means of Your servants; for we are not able to understand that which is good as you art, our Creator. 
但你确切地知道你借着你的仆人所做的事，因为我们不能明白你这造物主，你所行的善，是我们所不能明白的。
\Verse But again I will speak in Your presence, O \LORD, my \LORD. 
但耶和华啊，我的主啊，我要再一次在你面前说。
\Verse When of old there was no world with its inhabitants, you did devise and speak with a word, and forthwith the works of creation stood before you. 
从前世界没有居民的时候，你就用话语设计，说了一句话，造物的事就站在你面前。
\Verse And you did say that you wouldst make for Your world man as the administrator of Your works, that it might be known that he was by no means made on account of the world, but the world on account of him. 
你曾说过，你要为你的世界造人，作你工作的管理人，叫人知道他不是因着世界而造，而是因着他而造的世界。
\Verse And now I see that as for the world which was made on account of us, lo! it abides; but we, on account of whom it was made, depart.'
我现在看见，那因我们而造的世界，还在，但我们因着谁而造的，就离去了。

\Chapter
\Verse And the Lord answered and said unto me: 'You are rightly astonished regarding the departure of man, but you have not judged well regarding the evils which befall those who sin. 
主回答我说：'你对人的离去感到惊奇是对的，但你对那些犯罪的人所受的罪，却没有判断好。
\Verse And as regards what you have said, that the righteous are carried off and the impious are prospered, 
至于你所说的，义人被赶走，不虔诚的人被赶走，不虔诚的人被发扬光大，
\Verse And as regards what you have said: "Man knows not Your judgment "
至于你所说的。"人不知道你的审判"，
\Verse —On this account hear, and I will speak to you, and hearken, and I will cause you to hear My words. 
你要听，我就对你说，你要听，我就使你听，我就使你听我的话。
\Verse Man would not rightly have understood My judgment, unless he had accepted the law, and I had instructed him in understanding. 
人若不接受我的律法，我又指示他明白我的判断，他就不会明白我的判断。
\Verse But now, because he transgressed wittingly, yea, just on this ground that he knows (about it), he shall be tormented.
但现在，因为他故意犯了罪，是的，就因为他知道这一点，他就必受折磨。

\Verse And as regards what you did say touching the righteous, that on account of them has this world come, so also again shall that, which is to come, come on their account. 
至于你所说的关于义人的事，今世因着他们的缘故而来，将来要来的也要因着他们的缘故而来。
\Verse For this world is to them a strife and a labor with much trouble; and that accordingly which is to come, a crown with great glory.'
因为这世界对他们来说，是有许多的争战和劳苦，而那要来的，也是有大荣耀的冠冕。

\Chapter
\Verse  And I answered and said: '0 LORD, my Lord, lo! the years of this time are few and evil, and who is able in his little time to acquire that which is measureless'
我回答说：“啊，\神 啊！呜呼！
这个时代的岁月不多而且是邪恶的，谁能在他那微不足道的时间里，获得无量的东西？

\Chapter
\Verse And the Lord answered and said unto me: 'With the Most High account is not taken of time nor of a few years. 
耶和华回答我说：'在至高者那里，不以时间为数，也不以年数为数。
\Verse For what did it profit Adam that he lived nine hundred and thirty years and transgressed that which he was commanded Therefore the multitude of time that he lived did not profit him, but brought death and cut off the years of those who were born from him. wherein did Moses suffer loss in that he lived only one hundred and twenty years, and, inasmuch he was subject to Him who formed him, brought the law to the seed of Jacob, and lighted a lamp for the nation of Israel'
亚当活了九百三十年，犯了所吩咐的事，有什么好处呢。所以，他活了九百三十年，所活的时间多了，不但没有好处，反而使他死了，使从他生的人的年限断了。
摩西只活了一百二十岁，就在其中受了损失，因为他只活了一百二十岁，就在他受制于形成他、将律法带给雅各的后裔、为以色列国点亮了一盏灯的时候，他就受了损失。

\Chapter
\Verse  And I answered and said: 'He that lighted has taken from the light, and there are but few that have imitated him. But those many whom he has lighted have taken from the darkness of Adam and have not rejoiced in the light of the lamp.' 
我回答说：'那点灯的人从光中取走了，仿效他的人不多。但他所点燃的人中，有许多人是从亚当的黑暗中取来的，没有因灯的光而欢喜。

\Chapter
\Verse  And He answered and said unto me: 'Wherefore at that time he appointed for them a covenant and said:
 他回答我说："所以当时他为他们立了一个约，说：'看哪，我把生死放在你们面前。

        "Behold I have placed before you life and death,"
		看哪，我已把生死放在你们面前。

        And he called heaven and earth to witness against them.
		他召来了天和地，让他们作见证。

\Verse For he knew that his time was but short,
因为他知道，他的时间很短。

        But that heaven and earth endure always.
        但是，天和地永存。

\Verse        But after his death they sinned and transgressed,
但在他死后，他们就犯罪了，越了规。

        Though they knew that they had the law reproving (them),
		虽然他们知道，他们有法律的责备（他们）。

        And the light in which nothing could err,
		还有那道光，没有任何东西会出错。

        Also the spheres which testify, and Me.
		还有那见证的星辰，和我。

\Verse  Now regarding everything that is, it is I that judge, but do not you take counsel in your soul regarding these things, nor afflict thyself because of those which have been. 
现在，凡属我的事，是我在审判，但你不要在你的灵魂里为这些事作议论，也不要因过去的事而自责。
\Verse For now it is the consummation of time that should be considered, whether of business, or of prosperity, or of shame and not the beginning thereof. 
因为现在要看时间的长短，不管是事业的兴旺，还是荣华富贵，或者是耻辱，都要看时间的长短，而不是时间的开始。
\Verse Because if a man be prospered in his beginnings and shamefully entreated in his old age, he forgets all the prosperity that he had. 
因为人若是初时兴旺，年老时可耻地受人欺负，就忘记了他曾经的一切兴旺。
\Verse And again, if a man is shamefully entreated in his beginnings, and at his end is prospered, he remembers not again his evil entreatment. 
又说，人若是初时受了可耻的盘缠，到了晚年却得了丰盛，就不记得自己的恶行了。
\Verse And again hearken: though each one were prospered all that time—all the time from the day on which death was decreed against those who transgress—and in his end was destroyed, in vain would have been everything.'
你要再听着，从那日起，各人虽然一直都是富足的，但从那日起，死亡的人被判处死刑，到最后被消灭，一切的一切都是徒然的。
\par
20. Zion has been taken away to hasten the Advent of the Judgment
\par
锡安已被带走，审判又近了。
\par

\Chapter 
\Verse    'Therefore, behold! the days come,
'所以，看哪！日子到了。

        And the times shall hasten more than the former,
而时代要比前者更快。

        And the seasons shall speed on more than those that are past,
 季节的速度要比那些过去的季节更快。
 
        And the years shall pass more quickly than the present (years).
 岁月必比现在快。
 
\Verse  Therefore have I now taken away Zion,
因此，我现在已经夺去了锡安。

        That I may the more speedily visit the world in its season.
好叫我更快地到世界上的季节里去。

\Verse   Now therefore hold fast in your heart everything that I command you,
所以，现在你们要把我所吩咐你们的一切事，紧紧地记在心里。

      And seal it in the recesses of your mind.
并将它封在你的心底。

\Verse   And then I will show you the judgment of My might,
然后我将向你们展示我的大能的审判。

     And My ways which are unsearchable.
我的道，是不可寻觅的。

\Verse Go therefore and sanctify thyself seven days, and eat no bread, nor drink water, nor speak to anyone. 
所以你要去洁净自己七天，不吃饼，不喝水，也不与人说话。
\Verse And afterwards come to that place and I will reveal Myself to you, and speak true things with you, and I will give you commandment regarding the method of the times; for they are coming and tarry not.'
之后，到那地方去，我必向你们显明我，与你们说真话，并将时代的方法吩咐给你们，因为他们要来了，不要耽搁。

\par
21:1-11. Fast of seven Days: Baruch's Prayer: God's Answer
\par
The Prayer of Baruch the Son of Neriah.
\par
21:1-11.七天的禁食。巴录的祷告。神的回应
\par
尼雅之子巴录的祷告
\par
\Chapter
\Verse And I went there and sat in the valley of Kidron in a cave of the earth, and I sanctified my soul there, and I ate no bread, yet I was not hungry, and I drank no water, yet I thirsted not, and I was there till the seventh day, as He had commanded me. 
我就到那里去，在基德隆的山谷里，坐在地洞里，我就在那里使我的灵魂成圣，没有吃饼，也不饿，没有喝水，也不渴，照着神所吩咐的，一直到第七天。
\Verse And afterwards I came to that place where He had spoken with me. 
后来，我就到了祂曾与我说话的地方。
\Verse And it came to pass at sunset that my soul took much thought, and I began to speak in the presence of the Mighty One, and said: 
日落的时候，我的心思就多了，我就在全能者面前说话，说：'你们啊，你们所造的，是什么？
\Verse 'O you that have made the earth, hear me, that have fixed the firmament by the word, and have made firm the height of the heaven by the spirit, that have called from the beginning of the world that which did not yet exist, and they obey you. 
你们啊，创造了大地的，要听我说，你们用道定了天穹，用灵定了天的高，用灵定了天的高，从世界之初就呼召那还不存在的，他们就顺服你们。
\Verse you that have commanded the air by Your nod, and have seen those things which are to be as those things which you are doing. 
你以你的点头命令空中的人，并看见你所行的事，就是你所行的事。
\Verse you that rule with great thought the hosts that stand before you: also the countless holy beings, which you did make from the beginning, of flame and fire, which stand around Your throne you rule with indignation.
你以大意治理站在你面前的万物，你也以大意治理站在你的宝座周围的无数圣洁的众生，那是你从起初所造的火焰和火，你以忿怒治理他们。
\Verse To you only does this belong that you should do forthwith whatsoever you do wish. 
这事只属于你，你所要作的一切事，都要立即作。
\Verse Who causes the drops of rain to rain by number upon the earth, and alone knows the consummation of the times before they come; have respect unto my prayer. For 
那使雨滴按着数目降在地上的雨滴，只有你自己知道时辰未到，你要尊重我的祷告。
\Verse you alone are able to sustain all who are, and those who have passed away, and those who are to be, those who sin, and those who are to righteous [as living (and) being past finding out]. For you alone do live immortal and past finding out, and know the number of mankind. And if in time many have sinned, yet others not a few have been righteous.
只有你能养活一切已经过世的人，和已经过世的人，和将要过世的人，以及犯罪的人，和正直的人。因為你們確是不朽的，是不朽的，是過去的，是知道人類的數目的。如果有許多人犯了罪，而其他的人卻沒有幾個人是義人。
\par
21:12-18. Baruch's Depreciation of this Life.
\par
巴录对今生的贬抑
\par
\Chapter
\Verse you know where you preserve the end of those who have sinned, or the consummation of those who have been righteous. 
你们知道，你们要保存那些犯了罪的人的结局，或保存那些称义的人的结局。
\Verse  For if there were this life only, which belongs to all men, nothing could be more bitter than this.
因为若只有这生命，属于众人的，没有比这更苦的了。
\Verse       For of what profit is strength that turns to sickness,
因为力气归于疾病，有什么好处呢。

Or fullness of food that turns to famine,
或吃饱了就变成了饥荒。

Or beauty that turns to ugliness.
或者说是变美为丑。

\Verse  For the nature of man is always changeable. 
因为人的本性总是变化的。
\Verse  For what we were formerly now we no longer are and what we now are we shall not afterwards remain.  
因为我们以前是谁，现在就不再是谁，现在是谁，以后也不会再是谁。
\Verse  For if a consummation had not been prepared for all, in vain would have been their beginning. But regarding everything that comes from you do you inform me, and regarding everything about which I ask you, do you enlighten me.
因为若不是为众人预备了一个圆满的结局，他们的开始也是徒然的。但凡从你那里来的事，你都要告诉我；凡我问你的事，你也要告诉我。
\par
21:19-25. Baruch prays to God to hasten the Judgment and fulfill His Promise
\par
巴录祈求神加速审判，实现他的应许。
\par

\Verse How long will that which is corruptible remain, and how long will the time of mortals be prospered, and until what time will those who transgress in the world be polluted with much wickedness.
腐朽的东西还能存留多久，凡人的时间还能繁衍多久，直到什么时候，那些在世间越轨的人，才会被很多的恶行所污染。
\Verse Command therefore in mercy and accomplish all that you saidst you wouldst bring, that Your might may be made known to those who think that Your long-suffering is weakness. 
因此，在怜悯中命令，完成你所说的一切，使你的大能为那些认为你的长期忍耐是软弱的人所知道。
\Verse And show to those who know not, that everything that has befallen us and our city until now has been according to the long-suffering of Your power, because on account of Your name you have called us a beloved people. 
\Verse Bring to an end therefore henceforth mortality. 终结从此之后的死亡。
\Verse And reprove accordingly the angel of death, and let Your glory appear, and let the might of Your beauty be known, and let Sheol be sealed so that from this time forward it may not receive the dead, and let the treasuries of souls restore those which are enclosed in them. 
向那些不知道的人表明，我们和我们的城市所遭遇的一切，到现在为止，都是因着你的大能的长期忍耐，因为你因着你的名，称我们为爱民。
\Verse For there have been many years like those that are desolate from the days of Abraham and Isaac and Jacob, and of all those who are like them, who sleep in the earth, on whose account you did say that you had created the world. 
因为从亚伯拉罕、以撒、雅各和所有像他们一样的人，以及所有像他们一样睡在地上的人中，有许多年头像亚伯拉罕、以撒和雅各的日子一样荒凉，因为你说你创造了世界，是因着他们的缘故。
\Verse And now quickly show Your glory, and do not defer what has been promised by you.' 
现在赶紧把你的荣耀显露出来吧，不要把你应许的事推迟。
\Verse And (when) I had completed the words of this prayer I was greatly weakened.
而（当）我完成了这句祷告的话后，我的力量大为削弱。
\par
22—23. God's Reply to Baruch's Prayer. He will fulfill His Promise: Time needed for its Accomplishment:  Things must be judged in the Light of their Consummation (22). Till all Souls are born the End cannot come (23).
\par
22—23. 上帝对巴录的祷告的回应。祂必成就祂的应许：成就所需的时间。 事物必须根据其圆满的光来判断(22)。直到所有的灵魂都出生，末日才会到来(23)。
\par
\Chapter 
\Verse And it came to pass after these things that lo! the heavens were opened, and I saw, and power was given to me, and a voice was beard from on high, and it said unto me: 
在这事之后，天被开了，我看见了，有力量赐给我，有声音從高处传来，对我说：。
\Verse Baruch, Baruch, why are you troubled 
巴录，巴录，你为何要烦恼呢？
\Verse He who travels by a road but does not complete it, or who departs by sea but does not arrive at the port, can he be comforted 
行路却未走完，行海却未到港的人，能得到安慰吗？
\Verse Or he who promises to give a present to another, but does not fulfill it, is it not robbery 
或者说他答应给别人礼物，却不履行，这不是抢劫吗？
\Verse Or he who sows the earth, but does not reap its fruit in its season, does he not lose everything 
或者是播种的人，不在季节里收割果实，岂不是一无所有？
\Verse Or he who plants a plant unless it grows till the time suitable to it, does he who planted it expect to receive fruit from it 
或者说，种植一株植物，若未到合适的时节，种它的人如何指望从它身上得到果实？
\Verse Or a woman who has conceived, if she bring forth untimely, does she not assuredly slay her infant 
 者说，一个女人如果怀了孕，如果她生的不及时，她不一定会杀了她的孩子吗？
\Verse Or he who builds a house, if he does not roof it and complete it, can it be called a house Tell Me that first.'
或者他盖房子的人，如果他不把房子盖好，不把房子盖完，还能叫房子吗？
先告诉我。
\Chapter  
\Verse And I answered and said: Not so, O LORD, my Lord.' 
我回答说："耶和华啊，我的主啊。耶和华啊，我的主啊，不是这样的。
\Verse And He answered and said unto me: 'Why therefore are you troubled about that which you know not, and why are you ill at ease about things in which you are ignorant 
他回答我說：'你為什麼要為你所不知道的事而煩惱，又為什麼要為你所不知道的事而不安呢？
\Verse For as you have not forgotten the people who now are and those who have passed away, so I remember those who are appointed to come. 
因為你沒有忘記現在的人和已過去的人，我也沒有忘記要來的人。
\Verse Because when Adam sinned and death was decreed against those who should be born, then the multitude of those who should be born was numbered, and for that number a place was prepared where the living might dwell and the dead might be guarded. 
因為當亞當犯了罪，應當生的人被定了死罪，應當生的人的數目就被定了下來，為了這數目，就預備了一個地方，讓活人居住，讓死人看守。
\Verse Before therefore the number aforesaid is fulfilled, the creature will not live again [for My spirit is the creator of life], and Sheol will receive the dead. 
因此，在上述的數目完成之前，受造物必不復活，因為我的靈是生命的創造者。
\Verse And again it is given to you to hear what things are to come after these times. 
我又把它赐给你们，要你们听到这些日子以后的事。
\Verse For truly My redemption has drawn nigh, and is not far distant as aforetime.
因為我的救贖已經臨近了，而且像從前一樣遙遠。
\par
24. The coming Judgment
\par
24. 即将到来的审判
\par
\Chapter 
\Verse 'For behold! the days come and the books shall be opened in which are written the sins of all those who have sinned, and again also the treasuries in which the righteousness of all those who have been righteous in creation is gathered. 
因為看哪！日子來了，書本必被打開，書中寫著所有犯過罪的人的罪，又寫著所有在創世中稱義的人的義，也必被聚集在這裏。
\Verse For it shall come to pass at that time that you shall see—and the many that are with you—the long-suffering of the Most High, which has been throughout all generations, who has been long-suffering towards all who are born, (alike) those who sin and (those who) are righteous.' 
因為到了那時候，你們必看見至高者的長期忍耐，這忍耐是歷代以來的事，他對所有生而為人的人，對犯罪的人和稱義的人，都有長期的忍耐。
\Verse And I answered and said: 'But, behold! O Lord, no one knows the number of those things which have passed nor yet of those things which are to come. 
我回应说：“主啊，沒有人知道已經過去的事和將要來的事有多少。
\Verse For I know indeed that which has befallen us, but what will happen to our enemies I know not, and when you will visit Your works.'
因为我确实知道我们所遭遇的事，但我不知道我们的仇敌会怎样，也不知道你什么时候要看你的作为。”
\par
25—26. Sign of the coming Judgment
\par
25—26. 即将到来的审判的预兆
\par
\Chapter 
\Verse And He answered and said unto me: 'You too shall be preserved till that time till that sign which the Most High will work for the inhabitants of the earth in the end of days. 
他回答我说：'你们也要保存到那时候，直到至高者要为地上的居民所行的神迹。
\Verse This therefore shall be the sign. 
因此，這必是神蹟。
\Verse When a stupor shall seize the inhabitants of the earth, and they shall fall into many tribulations, and again when they shall fall into great torments. And it will come to pass when they say in their thoughts by reason of their much tribulation: "The Mighty 'One doth no longer remember the earth"—yes, it will come to pass when they abandon hope, that the time will then awake.'
當地上的居民被迷惑的時候，他們要落在許多苦難中，又要落在大苦難中。當他們因他們的苦難而在思想中說："我的主啊！"他們的心思，因他們的苦難，就會發生。"他們說：「大能的人不再記念地獄了，是的，當他們放棄希望的時候，那時，他們就會醒來。

\Chapter 
\Verse And I answered and said: 'Will that tribulation which is to be continue a long time, and will that necessity embrace many years'
我回答说：'那必经的磨难会不会持续很长的时间，那必经的磨难会不会持续很多年呢？
\par
26-30. The Twelve Woes that are to Come upon the Earth: The Messiah and the temporary Messianic Kingdom
\par
26-30. 将要降临在地球上的十二大灾难。弥赛亚和临时的救世主国度
\par
\Chapter 
\Verse And He answered and said unto me: 'Into twelve parts is that time divided, and each one of them is reserved for that which is appointed for it. 
他回答我说：'那时间被分成十二个部分，每一个部分都是为那指定的时间而预备的。
\Verse In the first part there shall be the beginning of commotions. 
在第一部分中，必有動亂的開始。
\Verse And in the second part (there shall be) slayings of the great ones. 
在第二部分中，必有大人物的杀戮。
\Verse And in the third part the fall of many by death. 
而在第三部分中，许多人将因死亡而倒下。
\Verse And in the fourth part the sending of the sword. 
在第四部分中剑将被送来。
\Verse And in the fifth part famine and the withholding of rain. 
第五部分是饥荒和雨季。
\Verse And in the sixth part earthquakes and terrors. 
第六部分是地震和恐怖。
\Verse [Wanting.] 
第七部分遗失。
\Verse And in the eighth part a multitude of specters and attacks of the Shedim. 
第八部分，大量的幽灵\footnote{Specters.}和鬼魔\footnote{Shedim.}将袭击. 
\Verse And in the ninth part the fall of fire. 
在第九部分，火雨。
\Verse And in the tenth part rapine and much oppression. 
第十部分是强暴和压迫。
\Verse And in the eleventh part wickedness and unchastity. 
第十一部分，邪恶和不贞。 
\Verse And in the twelfth part confusion from the mingling together of all those things aforesaid. 
第十二部分，由于上述所有的事情混杂在一起而造成的混乱。
\Verse For these parts of that time are reserved, and shall be mingled one with another and minister one to another. 
那时候的十二部分中仍在的将要互相助益、混杂一起。
\Verse For some shall leave out some of their own, and receive (in its stead) from others, and some complete their own and that of others, so that those may not understand who are upon the earth in those days that this is the consummation of the times.
有的人要留出自己的一些，从别人那里领受，有的人要把自己的和别人的也领受，使那些在地上的人不明白那日在地上的人，这就是时代的圆满。

\Chapter 
\Verse Nevertheless, whoever understands shall then be wise. 
那凡是明白的人，就必是聪明的。
\Verse For the measure and reckoning of that time are two parts a week of seven weeks.' 
因为那时候的时间是一个星期七周的两部分。
\Verse And I answered and said: 'It is good for a man to come and behold, but it is better that he should not come lest he fall. 
我回答说："人来看，是好的，但最好不要来，免得跌倒。
\Verse [But I will say this also: 
'但我也要这样说: 
\Verse Will he who is incorruptible despise those things which are corruptible, and whatever befalls in the case of those things which are corruptible, so that he might look only to those things which are not corruptible] 
那不朽坏的人，要轻视那些不朽坏的东西，和那些不朽坏的东西的遭遇，使他只顾着那些不朽坏的东西。] 
\Verse But if; O Lord, those things shall assuredly come to pass which you have foretold to me, so do you show this also unto me if indeed I have found grace in Your sight. 
但如果主啊，你向我所预言的那些事必成真，你也要向我表明，如果我在你的眼里找到了恩典，你也要向我表明。
\Verse Is it in one place or in one of the parts of the earth that those things are come to pass, or will the whole earth experience (them) '
這些事是在一個地方，還是在地裡的某一個地方，還是全地的人都要經歷這些事。

\Chapter 
\Verse And He answered and said unto me: 'Whatever will then befall (will befall) the whole earth; therefore all who live will experience (them). 
然后，他回答说。 而不管是什么样的事情，只要是活生生的人都会经历过。
\Verse For at that time I will protect only those who are found in those self-same days in this land. 
因為到了那時候，我必保護那些在這地的人。
\Verse And it shall come to pass when all is accomplished that was to come to pass in those parts, that the Messiah shall then begin to be revealed. 
等到那地方的事都成了的时候，弥赛亚就要开始显露出来。
\Verse And Behemoth shall be revealed from his place and Leviathan shall ascend from the sea, those two great monsters which I created on the fifth day of creation, and shall have kept until that time; and then they shall be for food for all that are left. 
比希米特\footnote{Behemoth.}必从他的地方显露出来，
利维坦\footnote{Leviathan.}必从海中升起，
这两只大怪兽是我在创世五日所造的，直到那时候为止。
\Verse The earth also shall yield its fruit ten-thousandfold and on each () vine there shall be a thousand branches, and each branch shall produce a thousand clusters, and each cluster produce a thousand grapes, and each grape produce a cor of wine. 
地上的果子也要结出一万倍的果子，每一株葡萄树上要有一千个枝子，每一枝子要结出一千个葡萄，每一株葡萄要结出一串葡萄，每一串葡萄要结出一串酒。
\Verse And those who have hungered shall rejoice: moreover, also, they shall behold marvels every day. 
那些饥饿的人必欢喜，而且，他们也必天天看见奇事。
\Verse For winds shall go forth from before Me to bring every morning the fragrance of aromatic fruits, and at the close of the day clouds distilling the dew of health. 
因为风必从我面前吹来，每天早晨必带着芳香的果子的香气，到了晚上必带着云朵，蒸馏出健康的露水。
\Verse And it shall come to pass at that self-same time that the treasury of manna shall again descend from on high, and they will eat of it in those years, because these are they who have come to the consummation of time.
那時候，甘露的寶庫必從高處再降下來，他們要在那年頭吃，因為他們是來到了時間的終點。

\Chapter 
\Verse And it shall come to pass after these things, when the time of the advent of the Messiah is fulfilled, that He shall return in glory.
在这些事之后，当弥赛亚来临的时候，他必在荣耀中再来。
\par
30:2-5. The Resurrection
\par
\par

\Verse Then all who have fallen asleep in hope of Him shall rise again. 
那时候，所有因盼望他而沉睡的人，必复活。
\Verse And it shall come to pass at that time that the treasuries will be opened in which is preserved the number of the souls of the righteous, and they shall come forth, and a multitude of souls shall be seen together in one assemblage of one thought, and the first shall rejoice and the last shall not be grieved. 
到了那时候，那时候要打开宝库，里面保存着义人的灵魂的数目，他们要出来，众人的灵魂要聚集在一起，一心一意，一心一意，先人要欢喜，后人要欢喜，不至于悲伤。
\Verse For they know that the time has come of which it is said, that it is the consummation of the times. 
因为他们知道所言的时候已经到了，那是时代的终结。
\Verse But the souls of the wicked, when they behold all these things, shall then waste away the more. 
但恶人的灵魂，当他们看见这一切的事，就会更加浪费。
\Verse For they shall know that their torment has come and their perdition has arrived.'
因为他们必知道他们的苦难已经来临，他们的灭亡已经到来。

\par
31—33. Baruch exhorts the People to prepare themselves for worse Evils
\par
31—33. 巴录告诫人们要准备好迎接更可怕的灾难。
\par
\Chapter 

\Verse And it came to pass after these things: that I went to the people and said unto them: 'Assemble unto me all your elders and I will speak words unto them.' 
我就到百姓那里去对他们说：'你们的长老都聚集到我这里来，我要对他们说的话。"你们的长老都到我这里来，我要对他们说的话。
\Verse And they all assembled in the valley of the Kidron. 
他们都聚集在汲沦河谷\footnote{Valley of the Kidron.
也被称为基顺河谷。
即现代之拿尔河谷（Wadi en-Nar）
}里。
\Verse And I answered and said unto them:
我对他们说：

Hear, O Israel, and I will speak to you,
以色列人啊，你要听我说，我就对你们说。

And give ear, O seed of Jacob, and I will instruct you.
雅各的后裔啊，你们要听从，我必指示你们。


\Verse        Forget not Zion,
不要忘记锡安，

But hold in remembrance the anguish of Jerusalem.
但要记念耶路撒冷的苦难。


\Verse        For lo! the days come,
因为日子来了。

When everything that is shall become the prey of corruption
当所有的一切都将成为腐败的猎物时

And be as though it had not been.
而且要像以前一样。

\Chapter 
\Verse 'But as for you, if you prepare your hearts, so as to sow in them the fruits of the law, it shall protect you in that time in which the Mighty One is to shake the whole creation. 
但就你们而言，若是预备你们的心，使你们的心种下律法的果子，就必在全能者要动摇全人类的时候，保护你们。
\Verse [Because after a little time the building of Zion will be shaken in order that it may be built again. 
因为过了一段时间，锡安的建筑就会被动摇，以便重新建造。
\Verse But that building will not remain, but will again after a time be rooted out, and will remain desolate until the time. 
但那建筑不会留下来，而是要在一段时间后再次被铲除，直到那时候为止。
\Verse And afterwards it must be renewed in glory, and perfected for evermore.] 
之后，它必须在荣耀中更新，并永远完美。] 
\Verse Therefore we should not be distressed so much over the evil which has now come as over that which is still to be. 
所以我们不应该为现在已经到来的罪恶而忧虑，也不应该为将要到来的罪恶而忧虑。
\Verse For there will be a greater trial than these two tribulations when the Mighty One will renew His creation. 
因为当全能者要更新他的创造的时候，必有比这两个苦难更大的试炼。
\Verse And now do not draw near to me for a few days, nor seek me till I come to you.' 
现在不要在这几天内靠近我，也不要找我，直到我到你那里去。
\Verse And it came to pass when I had spoken to them all these words, that I, Baruch, went my way, and when the people saw me setting out, they lifted up their voice and lamented and said : 
我对他们说了这些话后，我巴录就走我的路。当民众看我将要离去，便抬起嗓子，哀叹着说：
\Verse To where are you departing from us, Baruch, and are you forsaking us as a father who forsakes his orphan children, and departs from them
巴录，你要离开我们到哪里去呢，巴录，你要离开我们吗？
\Chapter
\Verse 'Are these the commands which your companion, Jeremiah the prophet, commanded you, and said unto you: "Look to this people till I go and make ready the rest of the brethren in Babylon against whom has gone forth the sentence that they should be led into captivity" And now if you also forsake us, it were good for us all to die before you, and then that you should withdraw from us.'
这些就是你的同伴耶利米先知对你说的命令吗？
他说
"你要看管好这百姓，直到我去准备好巴比伦的弟兄们，使他们的刑罚被引为奴仆。"
如果你也离弃我们，我们都死在你面前，那对我们都有好处，然后你就应该离开我们。
\par
34—35. Lament of Baruch
\par
34—35. 巴录的哀歌
\par
\Chapter 
\Verse And I answered and said unto the people: 'Far be it from me to forsake you or to withdraw from you, but I will only go unto the Holy of Holies to inquire of the Mighty One concerning you and concerning Zion, if in some respect I should receive more illumination: and after these things I will return to you.
我回答說：「我不離棄你們，也不離棄你們，但我只願到聖殿去，向全能者求告你們和錫安的事，如果在某些方面，我可以得到更多的啟示，我就必回到你們中間。

\Chapter 
\Verse And I, Baruch, went to the holy place, and sat down upon the ruins and wept, and said:
我，巴录，到了圣地，坐在废墟上哭，说：

\Verse        'O that mine eyes were springs,
啊，我的眼睛是泉水，

And mine eyelids a fount of tears.
而我的眼皮是泪水的泉源。

\Verse        For how shall I lament for Zion,
因为我如何为锡安哀叹。

And how shall I mourn for Jerusalem
我又该如何为耶路撒冷哀叹

\Verse        Because in that place where I am now prostrate,
因我正向那地拜倒

Of old the high priest offered holy sacrifices,
远古的大祭司献祭之地

And placed thereon an incense of fragrant odors.
那香料燃烧之地

\Verse        But now our glorying has been made into dust,
但现在我们的荣光已经化为尘埃。

And the desire of our soul into sand.'
和我们灵魂的欲望成了沙子。
\par
36—37. The Vision of the Forest, the Vine, the Fountain and the Cedar
\par
36—37. 林、藤、泉、杉的异象
\par
\Chapter 
\Verse And when I had said these things I fell asleep there, and I saw a vision in the night. 
當我說了這些話後，我就在那裏睡著了，我在夜裏看到一個異象。
\Verse And lo! a forest of trees planted on the plain, and lofty and rugged rocky mountains surrounded it, and that forest occupied much space. 
在平原上有一片樹林，周圍有高大的山峰，那樹林佔了許多地方。
\Verse And lo! over against it arose a vine, and from under it there went forth a fountain peacefully. 
有一棵藤蔓，在它的上方，有一棵葡萄树，从它的下面，有一个泉眼静静地流出来。
\Verse Now that fountain came to the forest and was (stirred) into great waves, and those waves submerged that forest, and suddenly they rooted out the greater part of that forest, and overthrew all the mountains which were round about it. 
那噴泉到了那林子裡，被激起了大浪，那些浪頭淹沒了那林子，忽然把那林子的大部份連根拔起，把四周的山都推倒了。
\Verse And the height of the forest began to be made low, and the top of the mountains was made low and that fountain prevailed greatly, so that it left nothing of that great forest save one cedar only. 
森林的高度开始变低，山的顶端也变低了，山的顶端也变低了，那泉眼大盛，使那大森林只剩下一棵雪松。
\Verse Also when it had cast it down and had destroyed and rooted out the greater part of that forest, so that nothing was left of it, nor could its place be recognized, then that vine began to come with the fountain in peace and great tranquility, and it came to a place which was not far from that cedar, and they brought the cedar which had been cast down to it. 
当它把那森林的大部分都毁坏了，并把它连根拔起，使它什么都不剩，也不能认出它的位置。这时，那藤蔓开始带着喷泉来了，它来到离那棵雪松不远的地方，他们把投下的雪松带到了那里。
\Verse And I beheld and lo! that vine opened its mouth and spoke and said to that cedar: Art you not that cedar which was left of the forest of wickedness, and by whose means wickedness persisted, and was wrought all those years, and goodness never. 
我看见了，那葡萄树张开嘴，对那雪松说："你不就是那棵雪松吗？ 邪恶的森林里留下的那棵雪松吗？
邪恶的手段一直存在，这些年来，邪恶一直在被破坏，而善良从来没有被破坏。
\Verse And you kept conquering that which was not yours, and to that which was your you did never show compassion, and you did keep extending your power over those who were far from you, and those who drew near you, you did hold fast in the toils of your wickedness, and you did uplift thyself always as one that could not be rooted out! 
你不斷地征服那不屬於你的，對於那屬於你的，你從來沒有表現出憐憫，你不斷地把你的力量伸向那些遠離你的人，和那些接近你的人，你在你的惡行中堅守著，你總是把自己當作不能被根除的人而奮起來。
\Verse But now your time has sped and your hour is come. 
但现在你的时间已经过去了，你的时候到了。
\Verse Do you also therefore depart, O cedar, after the forest, which departed before you, and become dust with it, and let your ashes be mingled together. 
雪松啊，你也要离去吧，雪松啊，在你之前离去的森林之后，和它一起成为尘土，让你的灰烬混在一起。
\Verse And now recline in anguish and rest in torment till your last time come, in which you will come again, and be tormented still more.'
现在你要在痛苦中躺下，在苦难中休息，直到你最后的时候来，你要再来，受更多的折磨。


\Chapter And after these things I saw that cedar burning, and the vine growing, itself and all around it, the plain full of unfading flowers. And I indeed awoke and arose.
做完这些事后，我看到那棵雪松在燃烧，藤蔓在生长，它自己和周围的一切，平原上开满了不褪色的花。我果然醒了，醒了过来。
\par
38—40. Interpretation of the Vision
\par
38—40. 对异象的解释
\par
\Chapter 

\Verse And I prayed and said: 'O LORD, my Lord, you do always enlighten those who are led by understanding. 
我祷告说："耶和华啊，我的主啊，你总是启迪那些被领悟的人。
\Verse Your law is life, and Your wisdom is right guidance. 
你的律法是生命，你的智慧是正确的指引。
\Verse Make known to me therefore the interpretation of this vision. 
請你將這異象的解釋告訴我。
\Verse For you know that my soul hath always walked in Your law, and from my (earliest) days I departed not from Your wisdom.'
因为你知道我的灵魂一直在你的律法中行走，从我的时代起，我就没有偏离你的智慧。
\Chapter 
\Verse And He answered and said unto me: 'Baruch, this is the interpretation of the vision which you have seen. 
他回答我说：'巴录，这是你所看见的异象的解释。
\Verse As you have seen the great forest which lofty and rugged mountains surrounded, this is the word. 
如同你所看到的大森林，那高高的山峰所包围的大森林，就是这话，这道。
\Verse Behold! the days come, and this kingdom will be destroyed which once destroyed Zion, and it will be subjected to that which comes after it. 
看哪！日子来了，这个曾经毁灭锡安的国度将被毁灭，它将受制于后来的国度。
\Verse Moreover, that also again after a time will be destroyed, and another, a third, will arise, and that also will have dominion for its time, and will be destroyed. 
而且，那也要在一段时间之后再被毁灭，另一个，第三个，也要兴起，那也要有统治权，也要被毁灭。
\Verse And after these things a fourth kingdom will arise, whose power will be harsh and evil far beyond those which were before it, and it will rule many times as the forests on the plain, and it will hold fast for times, and will exalt itself more than the cedars of Lebanon. 
在这些事之后，必有第四个国度兴起，其权势将比以前的国度更严酷、更邪恶，其统治的次数将多如平原上的森林，其统治的次数也将多如平原上的森林，其统治的次数也将多如黎巴嫩的雪松。
\Verse And by it the truth will be hidden, and all those who are polluted with iniquity will flee to it, as evil beasts flee and creep into the forest. 
真理必被它隐藏起来，所有被不义污染的人都要逃到它那里去，就像恶兽逃到森林里去，匍匐前进。
\Verse And it will come to pass when the time of its consummation that it should fall has approached, then the principate of My Messiah will be revealed, which is like the fountain and the vine, and when it is revealed it will root out the multitude of its host. 
等到了它毁灭的时候，它要倒下的时候，我的弥赛亚的主宰就会显露出来，就像泉水和葡萄树一样，当它显露出来的时候，要把它的主人的万物都根除。
\Verse And as touching that which you have seen, the lofty cedar, which was left of that forest, and the fact, that the vine spoke those words with it which you did hear, this is the word.
说起你所看到的，说起你所看到的，说起那片林子里残留的高大的雪松，说起你听到的那句话的藤蔓，这就是那句话。

\Chapter 
\Verse The last leader of that time will be left alive, when the multitude of his hosts will be put to the sword, and he will be bound, and they will take him up to Mount Zion, and My Messiah will convict him of all his impieties, and will gather and set before him all the works of his hosts. 
那时候，最后的领袖必被活捉，当他的众人被钉死在剑上，他将被捆绑起来，带他上锡安山，我的弥赛亚要将他的一切罪孽定罪，并将他的众人的行为都聚集在他面前。
\Verse And afterwards he will put him to death, and protect the rest of My people which shall be found in the place which I have chosen. 
然后，他要把他处死，保护我所选的地方，我的子民中的其他人。
\Verse And his principate will stand for ever, until the world of corruption is at an end, and until the times aforesaid are fulfilled.
他的主将永远站在那里，直到堕落的世界结束，直到上述的时代实现。 
\Verse This is your vision, and this is its interpretation.'
这是你的异象，这是对它的解释。
\par
41—42. The Destiny of the Apostates and of the Proselytes
\par
41—42. 叛教者的命运和传教士的命运
\par
\Chapter 
\Verse And I answered and said: 'For whom and for how many shall these things be or who will be worthy to live at that time 
我回答说："这些事要为谁，为多少人，或者说，到那时，谁有资格活着？
\Verse For I will speak before you everything that I think, and I will ask of you regarding those things which I meditate. 
因為我要在你們面前說出我所想的一切 我也要問你們我所想的那些事。
\Verse For lo! I see many of Your people who have withdrawn from Your covenant, and cast from them the yoke of Your law. 
因为我看见你的子民中，有许多人退出你的盟约 我看见许多你的百姓退出了你的盟约，从你的律法的枷锁中脱离了他们。
\Verse But others again I have seen who have forsaken their vanity, and fled for refuge beneath Your wings. 
但我又见过一些人弃绝了他们的虚荣，逃到你的翅膀下避难。
\Verse What therefore will be to them or how will the last time receive them 
因此，他们将如何对待他们，或者最后一次将如何接待他们？
\Verse Or perhaps the time of these will assuredly be weighed, and as the beam inclines will they be judged accordingly'
也许这些的时间肯定会被权衡，而随着天平的倾斜，他们也会相应地被判断出来。

\Chapter 
\Verse And He answered and said unto me: 'These things also will I show unto you. 
他回答说："我也要把这些事给你们看。
\Verse As for what you did say—"To whom will these things be, and how many (will they be) "—to those who have believed there shall be the good which was spoken of aforetime, and to those who despise there shall be the contrary of these things. 
至于你所说的话，"这些事要给谁，又要给多少人"--对那些信了的人，必有以前所讲的好，对那些轻视的人，必有这些事的反面。
\Verse And as for what you did say regarding those who have drawn near and those who have withdrawn this in the word. 
至於你們所說的，是關於那些親近的人，和那些在道上撤回這事的人。
\Verse As for those who were before subject, and afterwards withdrew and mingled themselves with the seed of mingled peoples, the time of these was the former, and was accounted as something exalted. 
至于那些之前是臣民的人，后来又退出来，与混杂民族的种子混在一起的人，这些人的时间是前者，被认为是高尚的。
\Verse And as for those who before knew not but afterwards knew life, and mingled (only) with the seed of the people which had separated itself, the time of these (is) the latter, and is accounted as something exalted. 
至于那些之前不知道但后来知道生命的人，与那些脱离了自己的民族的种子混合在一起，这些人的时间是后者，被认为是高尚的东西。
\Verse And time shall succeed to time and season to season, and one shall receive from another, and then with a view to the consummation shall everything be compared according to the measure of the times and the hours of the seasons. 
時間必繼承於時間，季節必繼承於季節，一個人必從另一個人身上得到，而後來，為了達到目的，一切都要根據時間和季節的時間來比較。
\Verse For corruption shall take those that belong to it, and life those that belong to it. 
因为腐败必夺去属于它的，生命也必夺去属于它的。
\Verse And the dust shall be called, and there shall be said to it: "Give back that which is not yours, and raise up all that you have kept until its time".'
尘土必被称为 "尘"，并对它说： "把不属于你的东西还给我，把你所保留的东西都拿出来，直到它的时间。"

\par 
Baruch told of his Death and bidden to give his last Commands to the People
\par
巴录讲述自己的死亡，并请他向人民发出最后的命令。
\par
\Chapter 
\Verse   But, do thou, Baruch, direct your heart to that which has been said to you,
但是，巴录，你要把你的心引向对你说过的话。

And understand those things which have been shown to you;
也要明白那些已经向你们显明的事。

For there are many eternal consolations for you.
因為有許多永恆的安慰，要賜給你們。

\Verse        For you shall depart from this place,
你們必從這地方離開。

And you shall pass from the regions which are now seen by you,
你们要从你们现在所看到的区域中经过。

And you shall forget whatever is corruptible,
而你要忘记任何腐朽的东西。

And shall not again recall those things which happen among mortals.
不要再回想那些发生在凡人之间的事。

\Verse Go therefore and command your people, and come to this place, and afterwards fast seven days, and then I will come to you and speak with you.'
所以你要去吩咐你的百姓，到这地方来，然后禁食七天，我就到你那里去与你说话。
\par
44:1-8; 45—46. Baruch tells the Elders of his impending Death, but encourages them to expect the Consolation of Zion
\par
巴录告诉长老们他即将死亡，但鼓励他们期待锡安的安慰。
\par
\Chapter 

\Verse And I, Baruch, went from thence, and came to my people, and I called my first-born son and [the Gedaliahs] my friends, and seven of the elders of the people, and I said unto them:
我巴录从那里去，来到我的族人那里，叫我的长子和我的朋友们，还有七位长老，我对他们说：

\Verse         Behold, I go unto my fathers
看哪，我到我的祖宗那里去了。

According to the way of all the earth.
按着全地的方式.

\Verse        But withdraw you not from the way of the law,
但你们不要离开律法的道路。

But guard and admonish the people which remain,
但守卫和告诫留下来的人。

Lest they withdraw from the commandments of the Mighty One.
免得他们背离全能者的诫命。

\Verse        For you see that He whom we serve is just,
因為你們看見我們所服事的人是公義的。

And our Creator is no respecter of persons.
我们的造物主是不尊重人的。

\Verse        And see you what hath befallen Zion,
你們看，錫安所遭遇的。

And what hath happened to Jerusalem.
你們看，耶路撒冷所发生的。

\Verse        For the judgment of the Mighty One shall (thereby) be made known,
因为全能者的审判，必使人知道。

And His ways, which, though past finding out, are right.
他的道，如以往所表现的一样，是正的。

\Verse        For if you endure and persevere in His fear,
因为如果你在他的敬畏中忍耐，坚持不懈，就会得到他的帮助。

And do not forget His law,
也不要忘记祂的律法。

The times shall change over you for good.
时代必改变你们的命运。

And you shall see the consolation of Zion.
你们必看到锡安的安慰。


\Verse, 
\Verse    Because whatever is now is nothing,
因为无论现在是什么，都不算什么。

But that which shall be is very great.
但那必有的事是非常大的。

For everything that is corruptible shall pass away,
因为凡是腐朽的东西，都将消逝。

And everything that dies shall depart,
一切死亡的东西都将离去。

And all the present time shall be forgotten,
而现在的时间都将被遗忘。

Nor shall there be any remembrance of the present time, which is defiled with evils.
也不应该有任何关于现在这个被邪恶玷污的时代的记忆。

\Verse      For that which runs now runs unto vanity,
因为现在的都不过是浮华。

And that which prospers shall quickly fall and be humiliated.
兴旺的，必迅速衰落，受辱。

\Verse      For that which is to be shall be the object of desire,
因为那要成为的，必成为欲望的对象。

And for that which comes afterwards shall we hope;
我们要为以后的事而盼望。

For it is a time that passes not away,
因為那是一個不會消失的时代。

\Verse      And the hour comes which abides for ever.
那時辰來了，是永遠的。

And the new world (comes) which does not turn to corruption those who depart to its blessedness,
而一个新的世界即将到来，不会使那些在其祝福中离去的人堕落。

And has no mercy on those who depart to torment,
并对那些离去受苦的人毫不留情。

And leads not to perdition those who live in it.
也不至于让生活在其中的人走向灭亡。

\Verse      For these are they who shall inherit that time which has been spoken of,
因為他們是要繼承所說的時代的人。

          And theirs is the inheritance of the promised time.
他们是应许时代的继承者。

\Verse      These are they who have acquired for themselves treasures of wisdom,
他们是为自己获得了智慧的宝藏。

          And with them are found stores of understanding,
 而有了他们，就有了理解的仓库。

          And from mercy have they not withdrawn,
怜悯尚未弃他们而去，

          And the truth of the law I have they preserved.
我的律法之真理也在他们中保全。

\Verse      For to them shall be given the world to come,
因为要把世界交给他们。

But the dwelling of the rest who are many shall be in the fire.'
但剩下的人多的住处，必在火中。

\Chapter 
\Verse 'Do you therefore so far as you are able instruct the people, for that labor is ours. For if you teach them, you will quicken them.'
'所以你们要尽你们的能力去教导百姓，因为那是我们的劳动。'因为你若教导他们，你就会使他们快些。

\Chapter 

\Verse And my son and the elders of the people answered and said unto me:
我的儿子和民众的长老们回应对我说：

'Has the Mighty One humiliated us to such a degree
'全能者把我们羞辱到这种程度了吗？

As to take you from us quickly
为了尽快把你从我们这里带走

\Verse        And truly we shall be in darkness,
而真正的我们将陷入黑暗中。

And there shall be no light to the people who are left,
也必将没有光亮的人离开。

\Verse        For where again shall we seek the law,
因为我们又该到哪里去寻求律法。

Or who will distinguish for us between death and life'
或者说，谁来为我们区分死与生"。

\Verse        And I said unto them: 'The throne of the Mighty One I cannot resist;
我对他们说 '全能者的寶座，我不能抗拒。

Nevertheless, there shall not be wanting to Israel a wise man
但在以色列人中，未有智慧的人。

Nor a son of the law to the race of Jacob.
这贤者也不出于雅各的后代。

\Verse        But only prepare you your hearts, that you may obey the law,
但只有准备好你们的心，才能让你们遵守法律。

And be subject to those who in fear are wise and understanding;
你要服从于那些有智慧和理解力的人。

And prepare your souls that you may not depart from them.
你們的靈魂要預備好，免得離開他們。

\Verse        For if you do these things, Good tidings shall come unto you.
因为你们若行这些事，必有好消息降临在你们身上。
[Which I before told you of; nor shall you fall into the torment, of which I testified to you before.' 
你们会落入我以前向你们见证的苦难之中。
\Verse But with regard to the word that I was to be taken I did not make (it) known to them or to my son.]
但我并未对儿子和长老们说我将被带走的消息。

\Chapter 
\Verse And when I had gone forth and dismissed them, I went there and said unto them: 'Behold! I go to Hebron: for thither the Mighty One hath sent me.' 
當我把他們打發走後，我就去那裡對他們說：
「我去希伯伦了，因为全能者已派我到那里去了。
\Verse And I came to that place where the word had been spoken unto me, and I sat there, and fasted seven days.
我来到了那个对我说过话的地方，我坐在那里，禁食了七天。
\par
48:1-47. PRAYER OF BARUCH
\par
48:1-47. 巴录的祷词
\par
\Chapter 
\Verse And it came to pass after the seventh day, that I prayed before the Mighty One and said
第七天之后，我在全能者面前祷告说

\Verse        'O my Lord, you summon the advent of the times,
"我的主啊，你召唤时代的来临。

And they stand before you;
他们站在你面前。

You cause the power of the ages to pass away,
你导致时代的力量消逝。

And they do not resist you;
而他们也不抗拒你。

          You arrange the method of the seasons,
你安排好了季节的方法。

And they obey you.
他们听从你的命令

\Verse        You alone know the duration of the generations,
只有你知道世世代代的长短。

And you reveal not Your mysteries to many.
你不向许多人透露你的奥秘。

\Verse        You make known the multitude of the fire,
 你使众人知道火之众。

And you weigh the lightness of the wind.
 你量测风之轻盈。

\Verse        You explore the limit of the heights,
你探知高的极限。

And you scrutinize the depths of the darkness.
你观察黑暗的深度。

\Verse        You care for the number which pass away that they may be preserved, And you prepare an abode for those that are to be.
你看顾逝去的人，使他们得以保存，你为将要逝去的人预备了一个居所。

\Verse        You remember the beginning which you have made,
你记得你所做的开端。

And the destruction that is to be You forget not.
你不会忘记将要发生的毁灭。

\Verse        With nods of fear and indignation You command the flames,
你指挥着火焰，恐惧和愤怒的点头听命，

And they change into spirits,
他们化为诸灵，

And with a word you quicken that which was not,
而你的一句话，就能让东西变得更快，

And with mighty power you hold that which has not yet come.
你用强大的力量掌握着那尚未到来的东西。

\Verse        You instruct created things in the understanding of you,
你让被造之物懂得你。

And you make wise the spheres so as to minister in their orders.
而你让球体聪慧，让他们听于号令服侍。

\Verse      Armies innumerable stand before you
無數的軍隊站在你面前

And minister in their orders quietly at Your nod.
在你点头的时候，静静地听从他们的命令。

\Verse      Hear Your servant
请听从你的仆人的命令

And give ear to my petition.
请听我的请求

\Verse      For in a little time are we born,
因为在无足轻重中，我们出生。

          And in a little time do we return.
又在无足轻重中，我们复归。

\Verse      But with you hours are as a time,
但你的分秒如长河

          And days as generations.
一日如数年。

\Verse      Be not therefore wroth with man; for he is nothing
所以不要与人争吵，因为他什么都不是。

\Verse      And take not account of our works; For what are we
也不要为我们作品骄傲，

For lo! by Your gift do we come into the world,
因为我们是靠你的恩赐来到这个世界上的。

          And we depart not of our own will.
 我们的离去不是出于我们自己的意愿。

\Verse      For we said not to our parents, "Beget us,
因为我们没有对我们的父母说："生我们"。

Nor did we send to Sheol and say, "Receive us."
我们也没有派人去阴间\footnote{Sheol.}说："接受我们"

\Verse      What therefore is our strength that we should bear Your wrath,
所以我们的力量是什么，我们应该承受你的愤怒

Or what are we that we should endure Your judgment
或者我们是什么，我们应该忍受你的审判？

\Verse      Protect us in Your compassions,
在你的慈悲中保护我们。

          And in Your mercy help us.
在你的怜悯中帮助我们

\Verse      Behold the little ones that are subject unto you,
看哪，看那受你支配的小人。

          And save all that draw near unto you:
拯救所有接近你的人

          And destroy not the hope of our people,
不要破坏我们人民的希望

          And cut not short the times of our aid.
并且不缩短我们援助的时间。

\Verse      For this is the nation which you have chosen,
因为这就是你所选择的国民。

          And these are the people, to whom you find no equal.
而这些人，你们找不到与他们同等的人。

\Verse      But I will speak now before you,
但我现在要在你们面前说：

          And I will say as my heart thinks.
我会照着我的心思说

\Verse      In you do we trust, for lo! Your law is with us,
我们相信你，因为你的律法与我们同在。你的律法与我们同在。

And we know that we shall not fall so long as we keep Your statutes.
我們知道，只要我們遵守你的規條，我們就不會跌倒。

\Verse      [To all time are we blessed at all events in this that we have not mingled with the Gentiles.]
我們在這事上不與外邦人混為一談，是有福的。

\Verse      For we are all one celebrated people,
因为我们都是一个值得庆贺的民族。

Who have received one law from One:
從一人，我们接受了一條律法。

And the law which is amongst us will aid us,
在我们中间的律法将帮助我们。

And the surpassing wisdom which is in us will help us.'
在我们里面的超凡的智慧必帮助我们。

\Verse And when I had prayed and said these things, I was greatly weakened.
當我禱告說這些話的時候，我就大為虛弱。
\Verse And He answered and said unto me: 
他回答我说：'

'You have prayed simply, O Baruch,
巴录啊，你的祷告是简单的。

And all your words have been heard.
你所说的一切话都已被听见了

\Verse      But My judgment exacts its own
但我的审判自有其力

And My law exacts its rights.
但我的律法自有其义

\Verse      For from your words I will answer you,
为从你的话中我将回答你。

And from your prayer I will speak to you.
从你的祈祷中，我将对你说话。

\Verse For this is as follows: he that is corrupted is not at all; he has both wrought iniquity so far as lie could do anything, and has not remembered My goodness, nor accepted My long-suffering. 
因为这话是这样说的，那败坏的人根本就不是，他既行了谎言所能行的不义之事，又不记念我的良善，也不接受我的忍耐。
\Verse Therefore you shall surely be taken up, as I before told you. 
因此，你們必如我先前所告訴你們的，必被帶上來。
\Verse For that time shall arise which brings affliction; for it shall come and pass by with quick vehemence, and it shall be turbulent coming in the heat of indignation. 
因為那時候必有苦難的時候，因為那時候必來了，必急速地來，急速地過去，必在憤怒的氣勢中湍急地來。
\Verse And it shall come to pass in those days that all the inhabitants of the earth shall be moved one against another, because they know not that My judgment has drawn nigh.
那日，地上所有的居民都要互相抵触，因为他们不知道我的审判已经临到。


\Verse      For there shall not be found many wise at that time,
因為那時必沒有許多智者。

          And the intelligent shall be but a few:
而有智慧的人只是少数。

          Moreover, even those who know shall most of all be silent.
而且，即使是知道的人，也必沉默不语。

\Verse      And there shall be many rumors and tidings not a few,
而且必有许多谣言和消息，而不是少数。

          And the doing of phantasms shall be manifest,
而所做的幻术，必将显现出来。

          And promises not a few be recounted,
应许将被多人重复。

          Some of them (shall prove) idle,
		    其中有的闲置。

          And some of them shall be confirmed.
他们中的一些人将被证实。

\Verse      And honor shall be turned into shame,
荣耀将变成耻辱。

          And strength humiliated into contempt,
		  而力量被羞辱蔑视。

And probity destroyed,
而廉洁也被破坏了。

And beauty shall become ugliness.
而美会变成丑陋。

\Verse      And many shall say to many at that time:
那时候，许多人要对许多人说：

"Where hath the multitude of intelligence hidden itself,
众人的智慧藏在哪里？

And whither hath the multitude of wisdom removed itself"
众生的智慧又从何而来"

\Verse      And whilst they are meditating these things,
当他们在冥想这些事情的时候，

Then envy shall arise in those who had not thought aught of themselves 
那么，那些不为自己着想的人，就会产生嫉妒

And passion shall seize him that is peaceful,
激情将夺取和平的人。

And many shall be stirred up in anger to injure many,
而许多人必被激起怒火，伤害许多人。

And they shall rouse up armies in order to shed blood,
他们要召集军队，以便流血。

And in the end they shall perish together with them.
到最后，他们也会和他们一起灭亡。


\Verse      And it shall come to pass at the self-same time,
而它将会在自已的时间内通过。

That a change of times shall manifestly appeal to every man,
时代的变迁，将明显地吸引着每一个人。

Because in all those times they polluted themselves
因为在那个时代，他们的污染了自己

And they practiced oppression,
而且他们实行的是压迫。

And walked every man in his own works,
并在自己的作品中走过每一个人。

And remembered not the law of the Mighty One.
也不记得全能者的律法。


\Verse      Therefore a fire shall consume their thoughts,
因此，火必吞噬他们的思想。


And in flame shall the meditations of their reins be tried;
在火焰中，他们的马缰绳的冥想将被审判。

For the Judge shall come and will not tarry.
因为审判者必来了，必不耽搁。


\Verse      Because each of the inhabitants of the earth knew when he was transgressing.因为地上的每一个居民都知道自己何时犯了罪。

But My Law they knew not by reason of their pride.
我的律法，確是因他們的驕傲而不知道。


\Verse      But many shall then assuredly weep,
但很多人都会流泪。

Yea, over the living more than over the dead.'
"是的，为活人比死人更多。


\Verse      And I answered and said:
我回答说

'O Adam, what have you done to all those who are born from you
亚当啊，你对所有从你而生的人做了什么？

And what will be said to the first Eve who hearkened to the serpent
而对于第一个听从蛇的夏娃，要怎么说呢？

\Verse      For all this multitude are going to corruption,
因为所有这些人都要去朽坏。

Nor is there any numbering of those whom the fire devours.
这些被火吞没的人无可计数。

\Verse But again I will speak in Your presence.
但我要再一次在你面前说话.  
\Verse You, O LORD, my Lord, know what is in Your creature. 
耶和华啊，我的主啊，你知道你的受造物里有什么。
\Verse For you did of old command the dust to produce Adam, and you know the number of those who are born from him, and how far they have sinned before you, who have existed and not confessed you as their Creator. 
因為你從前曾吩咐塵土製造亞當，你知道有多少從他生出的人，以及他們在你面前犯了多大的罪，他們在你面前有多大的罪，都是不承认你是造物主。
\Verse And as regards all these their end shall convict them, and Your law which they have transgressed shall requite them on Your day.'
至于这一切，他们的结局必定他们的罪，他们所犯的你的律法，必在你的日子里报答他们。
\par
48:48-50. Fragment of an Address of Baruch to the People
\par
48:48-50. 巴录对人民的讲话片段
\par

\Verse      ['But now let us dismiss the wicked and inquire about the righteous.
但现在，让我们罢免恶人，询问义人。

\Verse      And I will recount their blessedness
我将叙述他们的福分

And not be silent in celebrating their glory, which is reserved for them.
也不要在庆祝他们的荣耀时沉默，因为那是为他们保留的。

\Verse      For assuredly as in a little time in this transitory world in which you live, you have endured much labor,
因为在这短暂的时间里，你们在这短暂的世界里生活的时候，你们已经忍受了许多劳动。

So in that world to which there is no end, you shall receive great light.']
所以，在那没有尽头的世界里，你们将得到大光明。]
\par
49—52. The Nature of the Resurrection Body: the final Destinies of the Righteous and the Wicked
\par
49—52. 复活体的性质：义人和恶人的最终命运。
\par

\Chapter 
\Verse 'Nevertheless, I Will again ask from you, O Mighty One, yea, I will ask made all things.
"然而，全能者啊，我必再向你求，是的，我必求万物。

\Verse        "In what shape will those live who live in Your day
住在你的日子里的人，將以什麼形態生活？

Or how will the splendor of those who (are) after that time continue
或者说，那之后的辉煌将如何延续？

\Verse        Will they then resume this form of the present,
那么他们会不会恢复这种形式的现在。

And put on these entrammelling members,
并穿上这些委托的成员。

Which are now involved in evils,
现在涉及到了邪恶。

And in which evils are consummated,
而在其中的恶行也就在其中完成了。

Or will you perchance change these things which have been in the world
或者说，你是否会改变世界上的这些东西？

As also the world"
世界也是如此"

\Chapter 

\Verse And He answered and said unto me:
他回答我说：'

'Hear, Baruch, this word,
巴录，你听我说。

And write in the remembrance of your heart all that you shall learn.
并把你所学的东西都写在心中的记忆中。

\Verse        For the earth shall then assuredly restore the dead,
因為地裡的死人必會復活。

[Which it now receives, in order to preserve them].
[它现在接受的，是为了保存它们]。

          It shall make no change in their form,
它不得改变其形式。

But as it has received, so shall it restore them,
但它既然接受了，也要恢复他们。

And as I delivered them unto it, so also shall it raise them.
我将他们交给它，它也要使他们复活。

\Verse For then it will be necessary to show the living that the dead have come to life again, and that those who had departed have returned (again).
因為到了那時候，要讓活人知道，死人又復活了，離去的人又回來了。
\Verse And it shall come to pass, when they have severally recognized those whom they now know, then judgment shall grow strong, and those things which before were spoken of shall come.
當他們認清了他們現在所認識的人的時候，審判就必增長起來，以前所說的事也必來了。

\Chapter 
\Verse And it shall come to pass, when that appointed day has gone by, that then shall the aspect of those who are condemned be afterwards changed, and the glory of those who are justified. 
當那指定的日子過了，那被定罪的人的面目要變了，被稱義的人的榮耀也要變了。
\Verse For the aspect of those who now act wickedly shall become worse than it is, as they shall suffer torment. 
因为那些现在行恶的人的面目要比现在更坏，因为他们要受折磨。
\Verse Also (as for) the glory of those who have now been justified in My law, who have had understanding in their life, and who have planted in their heart the root of wisdom, then their splendor shall be glorified in changes, and the form of their face shall be turned into the light of their beauty, that they may be able to acquire and receive the world which does not die, which is then promised to them. 
至於那些在我的律法中稱職的人，他們的榮耀，他們的生命有了理解，在他們的心中種下了智慧的根，他們的榮耀必在變化中得到榮耀，他們的面孔的形狀必變成他們的光，使他們能得到和接受那不死的世界，那是應許給他們的。
\Verse For over this above all shall those who come then lament, that they rejected My law, and stopped their ears that they might not hear wisdom or receive understanding. 
因為那來的人，必在這上面哀嘆，因為他們拒絕了我的律法，停止了他們的耳朵，使他們不能聽到智慧，不能得到理解。
\Verse When therefore they see those, over whom they are now exalted, (but) who shall then be exalted and glorified more than they, they shall respectively be transformed, the latter into the splendor of angels, and the former shall yet more waste away in wonder at the visions and in the beholding of the forms. 
当他们看见那些现在被尊崇的人，他们现在被尊崇的人，后来又被尊崇的人，比他们更荣耀的人，他们必分别被改变，后者变成天使的光辉，前者必在异象和看形体的时候，更要在惊奇中消逝。
\Verse For they shall first behold and afterwards depart to be tormented.
因為他們必先看見，後來又要離開去受苦。

\Verse        But those who have been saved by their works,
但那些被他们的作品所拯救的人。

          And to whom the law has been now a hope,
		  而对谁来说，法律现在已经是一种希望。

          And understanding an expectation,
并理解一种期待。

          And wisdom a confidence,
智慧也是一种自信。

          Shall wonders appear in their time.
 奇迹将在他们的时代出现

\Verse        For they shall behold the world which is now invisible to them, 
因为他们要看到现在他们看不见的世界。 

          And they shall behold the time which is now hidden from them:
他们要看清时间，这时间已从他们身上隐去了。

\Verse        And time shall no longer age them.
时间将不再使他们衰老.

\Verse      For in the heights of that world shall they dwell,
因为在那世界的高处，他们必住在那里,

          And they shall be made like unto the angels,
他们将像天使一样被制造出来。

          And be made equal to the stars,
并使之与众星平等。

          And they shall be changed into every form they desire,
而他们将被改变成他们想要的各种形式。

          From beauty into loveliness,
从美丽变成可爱。

          And from light into the splendor of glory.
并从光辉中走进了辉煌。

\Verse For there shall be spread before them the extents of Paradise, and there shall be shown to them the beauty of the majesty of the living creatures which are beneath the throne, and all the armies of the angels, who are now held fast by My word, lest they should appear, and] are held fast by a command, that they may stand in their places till their advent comes. 
因為樂園的範圍必在他們面前擴張，在他們面前，必向他們顯現在寶座下的活物的威嚴之美，以及所有的天使的軍隊，都因我的話而堅守，免得他們顯現，又因命令而堅守，使他們在原地站立，直到他們的降臨。
\Verse Moreover, there shall then be excellency in the righteous surpassing that in the angels. 
而且，那时候，义人的尊贵必超过天使的尊贵。
\Verse For the first shall receive the last, those whom they were expecting, and the last those of whom they used to hear that they had passed away.
因为他们所盼望的人，先来的人要接待最后的人，最后的人要接待他们所盼望的人，他们常听说他们已经去世的人。

\Verse      For they have been delivered from this world of tribulation,
因为他们已经被从这个苦难的世界中解救出来了。

          And laid down the burthen of anguish.
并放下了痛苦的负担。

\Verse      For what then have men lost their life,
人为什么会失去生命呢？

          And for what have those who were on the earth exchanged their soul
那些在世间的人，用他们的灵魂换来了什么？

\Verse      For then they chose (not) for themselves this time,
他们这次不为自己，选择了

          Which, beyond the reach of anguish, could not pass away:
超出了痛苦的范围，无法消逝。

          But they chose for themselves that time,
但他们为自己选择了的

          Whose issues are full of lamentations and evils,
于是听他们充满哀伤和邪恶

          And they denied the world which ages not those who come to it,
他们否认了这个世界，而这个世界并没有让来到这个世界的人变老

          And they rejected the time of glory,
		  他们拒绝了荣耀的时代

          So that they shall not come to the honor of which I told you before.'
这样，他们就不会来参加我之前告诉你的荣誉了。

\Chapter 
\Verse And I answered and said:
我回答说。

'How can we forget those for whom woe is then reserved
我们怎么能忘记那些为他们保留了祸害的人呢？

\Verse        And why therefore do we again mourn for those who die
我们为什么又要为死去的人哀悼呢？

          Or why do we weep for those who depart to Sheol
又，我们为什么要为那些离去的人哭泣？

\Verse        Let lamentations be reserved for the beginning of that coming torment,
让我们把哀叹留给即将到来的苦难的开始。

          And let tears be laid up for the advent of the destruction of that time.
让眼泪为那时代的毁灭的来临而流下

\Verse        [But even in the face of these things will I speak.
但即使面对这些事，我也要说话。

\Verse        And as for the righteous, what will they do now
至于义人，他们现在要做什么？

\Verse        Rejoice you in the suffering which you now suffer:
你要为你现在所受的苦难而欢喜。

          For why do you look for the decline of your enemies
因为你们为什么要寻找你们的敌人的衰败？

\Verse        Make ready your soul for that which is reserved for you,
请准备好你的灵魂，为那为你保留的东西做好准备。

And prepare your souls for the reward which is laid up for you.']
准备好你的灵魂，要為那為你們所設立的賞賜而準備好。
\par
53—54. THE MESSIAH APOCALYPSE
\par
53—54. 弥赛亚的启示录
\par
53. The Vision of the Cloud with black and white Waters
\par
53. 黑白水的云之幻象
\par
\Chapter 
\Verse And when I had said these things I fell asleep there, and I saw a vision, and lo! a cloud was ascending from a very great sea, and I kept gazing upon it) and lo! it was full of waters white and black, and there were many colors in those self-same waters, and as it were the likeness of great lightning was seen at its summit. 
當我說了這些話後，我就在那裏睡著了，我看見異象，有一朵雲從大海中升起，我一直注視著它，那雲充滿了白色和黑色的水，在那相同的水裏有許多顏色，在它的頂上有大閃電的樣子。
\Verse And I saw the cloud passing swiftly in quick courses, and it covered all the earth. 
我看見那雲迅速地駛過來，覆蓋了全地。
\Verse And it came to pass after these things that that cloud began to pour upon the earth the waters that were in it. 
在这些事之后，那云开始把里面的水倒在地上。
\Verse And I saw that there was not one and the same likeness in the waters which descended from it. 
我看见从那云中降下的水，并没有一个相同的相似之处。
\Verse For in the first beginning they were black and many (Or a time, and afterwards I saw that the waters became bright, but they were not many, and after these things again I saw black (waters), and after these things again bright, and again black and again bright. 
因为刚开始的时候，它们又黑又多（或有一段时间，后来我看见水变亮了，但并不多，在这些东西之后，我又看见黑的（水），在这些东西之后，又是亮的，又是黑的，又是亮的。
\Verse Now this was done twelve times, but the black were always more numerous than the bright.
这样做了十二次，但黑的总是比亮的多。
\Verse And it came to pass at the end of the cloud, that lo! it rained black waters, and they were darker than had been all those waters that were before, and fire was mingled with them, and where those waters descended, they wrought devastation and destruction. 
到了云的尽头，就下起了黑色的水，比以前的水更黑，火也掺杂在其中，这些水降下的地方，就造成了破坏和毁灭。
\Verse And after these things I saw how that lightning which I had seen on the summit of the cloud, seized hold of it and hurled it to the earth. 
在这些事之后，我看见我在云顶上所看见的闪电，抓住了它，把它扔到地上。
\Verse Now that lightning shone exceedingly, so as to illuminate the whole earth, and it healed those regions where the last waters had descended and wrought devastation. 
那闪电照耀着大地，照亮了整个大地，使最后的水降下并造成破坏的地方得到了医治。
\Verse And it took hold of the whole earth, and had dominion over it. 
它占据了整个大地，统治了整个大地。
\Verse And I saw after these things, and lo! twelve rivers were ascending from the sea, and they began to surround that lightning and to become subject to it. 
我看见这些事之后，十二条河从海中升起，开始环绕着那闪电，并受其支配。
\Verse And by reason of my fear I awoke.
我因我的恐懼而醒來。
\par
54—55. Baruch's Prayer for an Interpretation of  the Vision: Ramiel's advent for this Purpose
\par
54—55. 巴录对异象的解释的祈祷。拉米勒为此目的而来
\par
\Chapter 
\Verse And I besought the Mighty One, and said:
我祈求全能者说：'我的主啊！'我求全能者说

'You alone, O \LORD, know of aforetime the deep things of the world,
主啊，只有你一个人知道世间深奥的事。

And the things which befall in their times You bring about by Your word, And against the works of the inhabitants of the earth you do hasten the beginnings of the times,
在他们的时代里发生的事，是你用你的话语使之发生的。
而对着地上的居民的劳作，你加速了时代的开端。

And the end of the seasons you alone know.
季节的尽头，只有你自己知道。

\Verse        (You) for whom nothing is too hard,
在你，没有什么是太难的。

But who do everything easily by a nod:
在你，点头之间事情得以成全。

\Verse        (You) to whom the depths come as the heights,
你深不见底，高不见顶。

And whose word the beginnings of the ages serve:
你的话语是世界万物的开端。

\Verse        (You) who reveal to those who fear you what is prepared for them,
你向那些敬畏你的人揭示了为他们准备的东西。

That thenceforth they may be comforted.
让他们得安慰。

\Verse        You show great acts to those who know not;
你向那些不知道的人展示了伟大的行为。

You break up the enclosure of those who are ignorant,
你打破了那些无知者的包围圈。

And lightest up what is dark,
照亮黑暗的东西。

And reveal what is hidden to the pure,
并向纯洁的人揭示隐藏的东西。

[Who in faith have submitted themselves to you and Your law.]
[因他们凭着信心将自己交给你和你的律法]

\Verse        You have shown to Your servant this vision;
你已经向你的仆人展示了这个异象。

Reveal to me also its interpretation.
也请你把它的解释告诉我。

\Verse        For I know that as regards those things wherein I besought you, I have received a response,
因为我知道，关于我求你的那些事，我已经得到了回应。

And as regards what I besought, you did reveal to me with what voice I should praise you,
因我的请求，你确实向我透露了我应该用什么声音来赞美你。

And from what members I should cause praises and hallelujahs to ascend to you.
我知晓了应当如何使赞美和哈利路亚升到你。

\Verse        For if my members were mouths,
因为如果我的肢体是口，

And the hairs of my head voices,
还有我头上的毛发的声音。

Even so I could not give you the reward of praise,
即使这样，我也不能给你的赞美奖励。

Nor laud you as is befitting,
也不夸奖你，因为这是很合适的。

Nor could I recount Your praise,
我也不能重述你的赞美。

Nor tell the glory of Your beauty.
也不诉说你的美貌的荣耀。

\Verse        For what am I amongst men,
我是茫茫众人之一，

Or why am I reckoned amongst those who are more excellent than I,
我为何在众人、比我更优秀的人中被认出？

That I have heard all these marvelous things from the Most High,
因我从至高者那里听到了这些奇妙的事情。

And numberless promises from Him who created me
还有来自创造我的神的无数应许

\Verse      Blessed be my mother among those that bear,
我的母亲是有福了

And praised among women be she that bare me.
赞美众女性中孕育了我的母亲。

\Verse      For I will not be silent in praising the Mighty One,
因为我不会在赞美大能者的时候沉默不语。

And with the voice of praise I will recount His marvelous deeds.
我要用赞美的声音叙述他的奇妙事迹。

\Verse      For who doeth like unto Your marvelous deeds, O God,
上帝啊，谁能像你所行的奇妙的事迹一样呢？

Or who comprehend Your deep thought of life.
或理解你对生命的深思熟虑的人。

\Verse      For with Your counsel you do govern all the creatures which Your right  hand has created
因为你用你的智慧管理你的右手所创造的一切生物。

And you have established every fountain of light beside you,
而你身边的每一个光之泉，都是你建立的。

And the treasures of wisdom beneath Your throne have you prepared.
而在你的宝座下的智慧宝藏，你已经准备好了。

\Verse      And justly do they perish who have not loved Your law,
不爱你的法律的人，他们就会义无反顾地灭亡。

And the torment of judgment shall await those who have not submitted themselves to Your power.
审判的苦难，必等待那些不顺从你的权势的人。

\Verse      For though Adam first sinned
亚当虽然先犯了罪。

And brought untimely death upon all,
并给所有人带来了不幸的死亡。

Yet of those who were born from him
但从他出生的人中

Each one of them has prepared for his own soul torment to come,
每一个人都为自己的灵魂煎熬做好了准备。

And again each one of them has chosen for himself glories to come.
而他们每一个人又一次为自己选择了即将到来的辉煌。

\Verse      [For assuredly he who believeth will receive reward.
因為信道的人，必得賞賜。

\Verse      But now, as for you, you wicked that now are, turn you to destruction, because you shall speedily be visited, in that formerly you rejected the understanding of the Most High.
但现在，你们这些恶人，要转而毁灭，因为你们以前拒绝了至高者的理解，你们必很快就会被拜访。

\Verse      For His works have not taught you,
因为他的作为没有教导你们。

Nor has the skill of His creation which is at all times persuaded you.]
祂所创造的技能也没有说服你们。]

\Verse      Adam is therefore not the cause, save only of his own soul,
亚当因此不是原因，只有他自己的灵魂才是原因。

But each of us has been the Adam of his own soul.
但是，我们每个人都是自己灵魂的亚当。

\Verse      But do You, O Lord, expound to me regarding those things which you have revealed to me,
主啊，求你向我说明你所启示给我的那些事。

And inform me regarding that which I besought you.
把我求你的事告诉我。


\Verse      For at the consummation of the world vengeance shall be taken upon those who have done wickedness according to their wickedness,
因为在世界末日的时候，那些行恶的人，必按他们的恶行而受到报复。

And you will glorify the faithful according to their faithfulness.
你要按着忠心的人的忠心荣耀他们。

\Verse      For those who are amongst your own you rule,
對於那些在你們中間的人，你們要統治他們。

And those who sin you blot out from amongst your own.'
而那些犯罪的人，你要把他们从你自己人中剔除。

\Chapter 
\Verse And it came to pass when I had finished speaking the words of this prayer, that I sat there under a tree, that I might rest in the shade of the branches. 
當我把這禱告的話說完了，我就坐在樹下，在樹枝的蔭下休息。

\Verse And I wondered and was astonished, and pondered in my thoughts regarding the multitude of goodness which sinners who are upon the earth have rejected, and regarding the great torment which they have despised, though they knew that they should be tormented because of the sin they had committed. 
我又惊奇，又思量着世上的罪人所拒绝的许多善事，以及他们所鄙视的巨大的苦难，虽然他们知道自己因所犯的罪要受苦，但他们所受的苦难，我却不知道。

\Verse And when I was pondering on these things and the like, lo! the angel Ramiel who presides over true visions was sent to me, and he said unto me:
当我在思索这些事和类似的事的时候，主宰异象的天使拉米勒被差遣到我这里来，对我说："我说：'你是我的朋友，我是你的朋友。

\Verse        'Why does your heart trouble you, Baruch,
巴录，你的心为什么会困扰着你？

and why does your thought disturb you
你的思绪为何困扰着你

\Verse        For if owing to the report which you have only heard of judgment you are so moved,
因为如果你只听过判决的报告，你就这么感动。

What (wilt you be) when you shall see it manifestly with your eyes
当你的眼睛看到它的时候，你会是什么？

\Verse        And if with the expectation wherewith you do expect the day of the Mighty One you are so overcome,
如果你們懷著期待的心態去期待全能者的日子，你們就這樣被征服了。

What (wilt you be) when you shall come to its advent
你会是怎样的人？

\Verse       And, if at the word of the announcement of the torment of those who have done foolishly you are so wholly distraught,
而且，如果在宣布那些愚昧的人所受的苦难的时候，你是如此地完全心烦意乱。

How much more when the event will reveal marvelous things
当活动将揭开奇迹的面纱时，会有多大的收获？

\Verse        And if you have heard tidings of the good and evil things which are then coming and are grieved,
如果你們聽到那時候的善事和惡事的音信，就會感到悲傷。

What (wilt you be) when you shall behold what the majesty will reveal, Which shall convict these and cause those to rejoice.'
當你們要看見那威嚴所揭示的事，必使他們定罪，使他們歡喜。
\par
56—74. Interpretation of the Vision. The black and bright Waters symbolize the World's History from Adam to the Advent of the Messiah.
\par
56—74. 对异象的解释。黑亮的水象征着从亚当到弥赛亚降临的世界历史。
\par
\Chapter 
\Verse 'Nevertheless, because you have besought the Most High to reveal to you the interpretation of the vision which you have seen, I have been sent to tell you. 
'然而，因为你们求至高者向你们揭示你们所看到的异象的解释，我被派来告诉你们。
\Verse And the Mighty One hath assuredly made known to you the methods of the times that have passed, and of those that are destined to pass in His world from the beginning of its creation even unto its consummation, of those things which (are) deceit and of those which (are) in truth. 
全能者確已將已經過去的時代的方法，以及從創世之初到終結，在他的世界中注定要過去的時代的方法，以及那些（是騙人的事，和那些（是真理的事）。
\Verse For as you did see a great cloud which ascended from the sea, and went and covered the earth, this is the duration of the world (= a) which the Mighty One made when he took counsel to make the world. 
因为你们看见一朵大云从海中升起，遮住了大地，这就是大能者造世界的时间。
\Verse And it came to pass when the word had gone forth from His presence, that the duration of the world had come into being in a small degree, and was established according to the multitude of the intelligence of Him who sent it. 
当那话从他的面前传来的时候，世界的期限已经在很小的程度上产生了，并按着那差遣它的人的智慧的多寡而建立了。
\Verse And as you did previously see on the summit of the cloud black waters which descended previously on the earth, this is the transgression wherewith Adam the first man transgressed.
你們先前在雲頂上所見的黑水，就是先前降在地上的黑水，這是第一個人亞當所犯的罪。


\Verse        For [since] when he transgressed
因为当他违背了

Untimely death came into being,
不期而遇的死亡，就这样应运而生了。

Grief was named
悲伤被命名

And anguish was prepared,
而苦恼是有准备的。

And pain was created,
痛苦也就产生了。

And trouble consummated,
而麻烦也就解决了。

And disease began to be established,
疾病开始了

And Sheol kept demanding that it should be renewed in blood,
阴间将一直由新鲜的血侍奉

And the begetting of children was brought about,
生儿育女的事情就这样产生了。

And the passion of parents produced,
父母的激情生产

And the greatness of humanity was humiliated,
人类的伟大也被羞辱了

And goodness languished.
善良也就无精打采了


\Verse What therefore can be blacker or darker than these things 
因此，有什么东西能比这些东西更黑、更暗呢？

\Verse This is the beginning of the black waters which you have seen. 
这就是你们所看到的黑水的开始。

\Verse And from these black (waters) again were black derived, and the darkness of darkness was produced. 
从这些黑水中又衍生出了黑色，并产生了黑暗的黑暗。

\Verse For he became a danger to his own soul: even to the angels 
因为他成为他自己的灵魂的危险，甚至是天使的危险。

\Verse For, moreover, at that time when he was created, they enjoyed liberty. 
而且，在他被创造的时候，他们享受着自由。

\Verse And became he a danger some of them descended, and mingled with the women. 
他的子嗣和女人混杂在一起，成为危险的开端。

\Verse And then those who did so were tormented in chains. 
这样做的人就被用铁链折磨着 

\Verse But the rest of the multitude of the angels, of which there is (no) number, restrained themselves. 
但其余的众天使中的众人，没有人数，都是自制的。

\Verse And those who dwelt on the earth perished together (with them) through the waters of the deluge. 
那些住在地上的人，因着大洪水的水，也一同灭亡了。

\Verse These are the black first waters.
这就是黑色的第一道水。

\Chapter 
\Verse And after these (waters) you did see bright waters: this is the fount of Abraham, also his generations and advent of his son, and of his son's son, and of those like them. 
在这些（水）之后，你们确实看到了明亮的水：这是亚伯拉罕的泉眼，也是他儿子的世代和临到的泉眼，也是他儿子的儿子的儿子，以及那些像他们一样的人的泉眼。

\Verse Because at that time the unwritten law was named amongst them,
因为在那个时候，不成文的法律在他们当中是有名字的。

And the works of the commandments were then fulfilled,
而戒律的工作也随之应验了。

And belief in the coming judgment was then generated,
于是就产生了对即将到来的审判的信念。

And hope of the world that was to be renewed was then built up,
而这时，这个世界即将更新的希望就这样建立起来了。

And the promise of the life that should come hereafter was implanted.
并许下了以后应该有的生命的承诺，被植入了。

\Verse        These are the bright waters, which you have seen.
这便是那明水，如你所见

\Chapter 
\Verse 'And the black third waters which you have seen, these are the mingling of all sins, which the nations afterwards wrought after the death of those righteous men, and the wickedness of the land of Egypt, wherein they did wickedly in the service wherewith they made their sons to serve. 
你们所看见的第三黑水，就是那些义人死后，万国所造的一切罪孽的混合，和埃及地的恶行，他们在埃及地作恶多端，使他们的儿子们在那里作恶多端的侍奉。

\Verse Nevertheless, these also perished at last.
然而，这些人最后也灭亡了。

\Chapter 
\Verse 'And the bright fourth waters which you have seen are the advent of Moses and Aaron and Miriam and Joshua the son of Nun and Caleb and of all those like them. 
你们所看见的第四水，就是摩西、亚伦、米利暗、约书亚的儿子和迦勒和所有像他们一样的人的降临。

\Verse For at that time the lamp of the eternal law shone on all those who sat in darkness, which announced to them that believe the promise of their reward, and to them that deny, the torment of fire which is reserved for them. 
因為那時候，永恆律法的燈照耀所有坐在黑暗中的人，向那些相信的人宣告賞賜的應許，也向那些不相信的人宣告，為他們預備的火刑。

\Verse But also the heavens at that time were shaken from their place, and those who were under the throne of the Mighty One were perturbed, when He was taking Moses unto Himself. 
但那时候，天也从他们的位置上摇动了，那些在大能者宝座下的人也被惊动了，因为他要把摩西带到自己面前。

\Verse For He showed him many admonitions together with the principles of the law and the consummation of the times, as also to you, and likewise the pattern of Zion and its measures, in the pattern of which the sanctuary of the present time was to be made. 
因為祂向他顯示了許多誡命，以及律法的原則和時代的結束，也向你們顯示了許多誡命，也向你們顯示了錫安的模式和措施，今時今日的聖所要以這個模式為基礎。

\Verse But then also He showed to him the measures of the fire, also the depths of the abyss, and the weight of the winds, and the number of the drops of rain: 
但他又向他显明了火的度量，深渊的深度，风的重量，雨滴的数目。

\Verse And the suppression of anger, and the multitude of long-suffering, and the truth of judgment: 
和愤怒的抑制，和众多的忍耐，和审判的真理。

\Verse And the root of wisdom, and the riches of understanding, and the fount of knowledge: 
和智慧的根，和理解的丰富，和知识的泉源。

\Verse And the height of the air, and the greatness of Paradise, and the consummation of the ages, and the beginning of the day of judgment: 
和天空之高、神国之伟大、时光之漫长与审判的开始：

\Verse And the number of the offerings, and the earths which have not yet come: 
和祭品的数目，和还没有到来的大地

\Verse And the mouth of Gehenna, and the station of vengeance, and the place of faith, and the region of hope: 
地狱之口，复仇的地方，信仰的地方，希望的地方。

\Verse And the likeness of future torment, and the multitude of innumerable angels, and the flaming hosts, and the splendor of the lightnings, and the voice of the thunders, and the orders of the chiefs of the angels, and the treasuries of light, and the changes of the times, and the investigations of the law. 
还有未来的苦难的样子，无数的天使，无数的天使，火焰的主人，闪电的光辉，雷电的声音，天使的首领的命令，光明的宝库，时代的变化，和律法的调查。

\Verse These are the bright fourth waters which you have seen.
这些是你们所看到的光明第四水。

\Chapter 
\Verse And the black fifth waters which you have seen raining are the works which the Amorites wrought, and the spells of their incantations which they wrought, and the wickedness of their mysteries, and the mingling of their pollution. 
你们所看见的第五黑水，就是亚摩利人所行的事，他们所行的咒语，他们所行的咒语，他们所行的咒语，他们所行的奥秘的邪恶，他们所行的污染。

\Verse But even Israel was then polluted by sins in the days of the judges, though they saw many signs which were from Him who made them.
但在审判者的日子里，以色列人也被罪孽污染了，虽然他们看见许多神迹，都是从创造他们的神那里来的。

\Chapter 
\Verse And the bright sixth waters which thru did see, this is the time in which David and Solomon were born.
你所见的第六道明水是大卫和所罗门出生的时候

\Verse        And there was at that time the building of Zion,
在那时候，锡安城兴建。

And the dedication of the sanctuary,
圣所被建立。

          And the shedding of much blood of the nations that sinned then,
		  而当时犯罪的国家流下了许多血的血。

And many offerings which were offered then in the dedication of the sanctuary.
还有许多献上的祭品，在当时献上的圣所。

\Verse        And peace and tranquility existed at that time,
在那时候，和平与安宁是存在的。

\Verse        And wisdom was heard in the assembly:
而智慧在会众中被听见。

          And the riches of understanding were magnified in the congregations,
智慧的丰富在会众中被放大了。

\Verse        And the holy festivals were fulfilled in blessedness and in much joy.
圣洁的节庆在祝福和喜乐中得到了满足。

\Verse        And the judgment of the rulers was then seen to be without guile,
然後統治者的審判就被看成是沒有惡意的。

And the righteousness of the precepts of the Mighty One was accomplished with truth.
并以真理成就了大能者的戒律的正道。

\Verse        And the land [which] was then beloved by the Lord,
这被神爱着的土地

And because its inhabitants sinned not, it was glorified beyond all lands, And the city Zion ruled then over all lands and regions.
因為它的居民沒有犯罪，所以它的榮耀超越了所有的土地。


\Verse        These are the bright waters which you have seen.
这便是你所见的明水。

\Chapter 
\Verse And the black seventh waters which you have seen, this is the perversion (brought about) by the counsel of Jeroboam, who took counsel to make two calves of gold: 
你们所看见的第七黑水，就是耶罗波安的劝告所带来的，这就是耶罗波安的劝告所带来的变态，他的劝告是要用金子做两个小牛犊。

\Verse And all the iniquities which kings who were after him iniquitously wrought. 
和一切跟随他的君王们所行的不义之事。

\Verse And the curse of Jezebel and the worship of idols which Israel practiced at that time. 
还有以色列人当时所行的耶洗别的咒诅和拜偶像的事。

\Verse And the withholding of rain, and the famines which occurred until women eat the fruit of their wombs. 
还有不降雨，和饥荒，直到妇女吃了他们肚子里的果子。

\Verse And the time of their captivity which came upon the nine tribes and a half, because they were in many sins. 
還有他們被囚禁的時候，因為他們有許多罪孽，所以九支派半被囚禁。

\Verse And Shalmanezzar king of Assyria came and led them away captive. 
亚述王夏尔玛尼撒来了，把他们掳走了。

\Verse But regarding the Gentiles it were tedious to tell how they always wrought impiety and wickedness, and never wrought righteousness. 
但关于外邦人，说起外邦人...... ...他们总是作恶多端，作恶多端，从没有作过公义。

\Verse These are the black seventh waters which you have seen.
这就是你们所看见的黑第七水。

\Chapter 
\Verse 'And the bright eighth waters which you have seen, this is the rectitude and uprightness of Hezekiah king of Judah and the grace (of God) which came upon him. 
你们所看见的第八水，这就是犹大王希西家的正直和正直，也是神的恩典临到他身上。

\Verse For when Sennacherib was stirred up in order that he might perish, and his wrath troubled him in order that he might thereby perish, for the multitude also of the nations which were with him. 
因為當西拿雪利被激起來，為了使他滅亡，他的憤怒使他憂心忡忡，為了與他同在的眾國的眾人，也為了使他滅亡。

\Verse When, moreover, Hezekiah the king heard those things which the king of Assyria was devising, (i.e.) to come and seize him and destroy his people, the two and a half tribes which remained: nay, more he wished to overthrow Zion also: then Hezekiah trusted in his works, and had hope in his righteousness, and spoke with the Mighty One and said: 
當希西家王聽到亞述王所設計的事，要來奪取他的百姓，毀滅他所剩的兩個半支派，更要推翻錫安。

\Verse "Behold, for lo! Sennacherib is prepared to destroy us, and he will be boastful and uplifted when he has destroyed Zion."
看哪，因為他們說："看哪，因為我的意思是說 西拿雪利准备毁灭我们，当他毁灭锡安的时候，他必自夸、自高自大。"

\Verse        And the Mighty One heard him, for Hezekiah was wise,
全能者听了他的话，因为希西家是有智慧的。

And He had respect unto his prayer, because he was righteous.
他对他的祷告很尊敬，因为他是公义的。

\Verse And thereupon the Mighty One commanded Ramiel His angel who speaks with you. 
于是，全能者吩咐与你说话的天使拉米勒。

\Verse And I went forth and destroyed their multitude, the number of whose chiefs only was a hundred and eighty-five thousand, and each one of them had an equal number (at his command). 
我就去消灭了他们的众人，他们的首领只有十万八千五千人，他们中的每一个人都有同样的人数。

\Verse And at that time I burned their bodies within, but their raiment and arms I preserved outwardly, in order that the still more wonderful deeds of the Mighty One might appear, and that thereby His name might be spoken of throughout the whole earth. 
那时，我把他们的身体烧毁，但他们的衣服和武器，我却把他们的衣服和武器保存在外面，以便大能者更奇妙的事迹显现出来，使他的名传遍全地。

\Verse And Zion was saved and Jerusalem delivered: Israel also was freed from tribulation. 
锡安得救了，耶路撒冷也得救了。以色列也从苦难中解脱出来。

\Verse And all those who were in the holy land  rejoiced, and the name of the Mighty One was glorified so that it was spoken of 
所有在圣地的人都欢喜，全能者的名也得着荣耀，使全能者的名得以传扬。

\Verse These are the bright waters which you have seen.
这些是你所见过的明亮的水。

\Chapter 
\Verse 'And the black ninth waters which you have seen, this is all the wickedness which was in the days of Manasseh the son of Hezekiah. 
你们所看见的第九黑水，就是希西家的儿子玛拿西的日子里所有的恶行。

\Verse For he wrought much impiety, and he slew the righteous, and he wrested judgment, and he shed the blood of the innocent, and wedded women he violently polluted, and he overturned the altars, and destroyed their offerings, and drove forth their priests lest they should minister in the sanctuary. 
因为他行了许多不义之事，杀了义人，夺取了审判，流了无辜的血，玷污了无辜的妇人，打翻了祭坛，毁坏了祭品，赶走了祭司，免得他们在圣所里作工。

\Verse And he made an image with five faces: four of them looked to the four winds, and the fifth on the summit of the image as ah adversary of the zeal of the Mighty One. 
他制造了一个五张面孔的形象，其中四张面孔望着四风，第五张面孔在形象的顶点上，作为全能者的狂热的对手。

\Verse And then wrath went forth from the presence of the Mighty One to the intent that Zion should be rooted out, as also it befell in your days. But also against the two tribes and a half went forth a decree that they should also be led away captive, as you have now seen. 
然后从全能者的面前发怒，要把锡安连根拔起，正如在你们的时代，也是如此。但又对那两个半支派下达了命令，要把他们也带去当俘虏，正如你们现在所看到的那样。

\Verse And to such a degree did the impiety of Manasseh increase, that it removed the praise of the Most High from the sanctuary. 
玛拿西的不义愈来愈大，使至高者的赞美从圣所中消失了。

\Verse On this account Manasseh was at that time named 'the impious," and finally his abode was in the fire. 
玛拿西在那时候被称为 "不虔诚的人"，最后他的居所被烧毁了。

\Verse For though his prayer was heard with the Most High, finally, when he was cast into the brazen horse and the brazen horse was melted, it served as a sign unto him for the hour. 
因为他的祷告虽然被至高者听见了，但最后，当他被扔在烈马上，烈马被融化的时候，对他来说，这也是一个标志。

\Verse For he had not lived perfectly, for he was not worthy—but that thenceforward he might know by whom finally he should be tormented. 
因为他没有完全活得好，因为他不配，但从此以后，他可以知道他最后该受谁的折磨。

\Verse For he who is able to benefit is also able to torment.
因为他能得益处，也能受折磨。

\Chapter 
\Verse 'Thus, moreover, did Manasseh act impiously, and thought that in his time the Mighty One would not inquire into these things. 
'因此，玛拿西的行为很不虔诚，以为在他的时代，全能者不会探究这些事。

\Verse These are the black ninth waters which you have seen.
这些是你们所看见的黑九水。

\Chapter 
\Verse 'And the bright tenth waters which you have seen: this is the purity of the generations of Josiah king of Judah, who was the only one at the time who submitted himself to the Mighty One with all his heart and with all his soul. 
你们所看见的那明亮的第十水，这就是犹大王约西亚王的世代的纯洁，他是当时唯一一个全心全意、全心全意顺服于大能者的人。
\Verse And he cleansed the land from idols, and hallowed all the vessels which had been polluted, and restored the offerings to the altar, and raised the horn of the holy, and exalted the righteous, and honored all that were wise in understanding, and brought back the priests to their ministry, and destroyed and removed the magicians and enchanters and necromancers from the land. 
他洁净了那地，使那地脱离偶像，使一切被污染的器皿成圣，使祭品恢复到坛上，升起圣人的角，赞美义人，尊崇义人，尊崇一切有智慧的人，使祭司们回到他们的道上，把巫师、巫师和巫师都从那地上消灭，并除去。
\Verse And not only did he slay the impious that were living, but they also took from the sepulchers the bones of the dead and burned them with fire. 
他不仅杀了活人中的不虔诚的人，而且他们还从棺材里取出死人的骨头，用火烧了他们。
\Verse [And the festivals and the Sabbaths he established in their sanctity], and their polluted ones he burnt in the fire, and the lying prophets which deceived the people, these also he burnt in the fire, and the people who listened to them when they were living, he cast them into the brook Kidron, and heaped stones upon them. 
他確立的節日和安息日，和污穢的節日，以及欺騙百姓的謊言先知，都被他燒在火中。
那些听信了谎言的民，也被他扔进了汲伦溪，又放置石头压住他们。
\Verse And he was zealous with zeal for the Mighty One with all his soul, and he alone was firm in the law at that time, so that he left none that was uncircumcised, or that wrought impiety in all the land, all the days of his life. 
他全心全意地热心于全能者，那时只有他一个人在律法上坚守，使他一生中没有一个人不受割礼，也没有一个人在全地行不义之事。
\Verse Therefore he shall receive an eternal reward, and he shall be glorified with the Mighty One beyond many at a later time. 
所以他必得永生的赏赐，以后必与大能者同享荣耀，胜过许多人。
\Verse For on his account and on account of those who are like him were the honorable glories, of which you were told before, created and prepared. These arc the bright waters which you have seen.
因为因着他和那些像他一样的人的功劳，就是你们以前所知道的荣耀，被创造和预备的荣耀。这些是你们所看见的明水。

\Chapter 
\Verse 'And the black eleventh waters which you have seen: this is the calamity which is now befalling "Zion.
而你们所看见的黑色第十一水：这就是现在降临在锡安的灾祸。

\Verse        Do you think that there is no anguish to the angels in the presence of the Mighty One,
你以为在大能者面前，天使们就没有苦恼吗。

That Zion was so delivered up,
那锡安就这样被送了上来。

And that lo! the Gentiles boast in their hearts,
外邦人在心里夸夸其谈。

And assemble before their idols and say,
并在他们的偶像面前集合，说：

          "She is trodden down who oftentimes trod down,
          "她是被人踩踏过的人。

And she has been reduced to servitude who reduced (others)"
她已经被贬为奴才了，是谁贬低了（别人）"

\Verse        Dost you think that in these things the Most High rejoices,
你以为在这些事情上，至高者会欢喜吗？

Or that His name is glorified
或者说祂的名被荣耀了

\Verse        [But how will it serve towards His righteous judgment]
[但它将如何为他的公义审判服务]

\Verse        Yet after these things shall the dispersed among the Gentiles be taken hold of by tribulation,
然而，在这些事之后，外邦人中的散居者必被磨难所掌握。

And in shame shall they dwell in every place.
他们必住在各处的耻辱中。

\Verse        Because so far as Zion is delivered up
因为只要锡安被送上来了

And Jerusalem laid waste,
而耶路撒冷也被浪费了。

Shall idols prosper in the cities of the Gentiles,
偶像要在外邦人的城市中繁荣起来吗？

And the vapor of the smoke of the incense of the righteousness which is by the law is extinguished in Zion,
而公义的香火之气的烟气，在锡安也就熄灭了。

And in the region of Zion in every place lo! there is the smoke of impiety.
在锡安地区的每一个地方，都有不虔诚的烟雾。

\Verse        But the king of Babylon will arise who has now destroyed Zion,
但巴比伦的王将兴起，他现在已经毁灭了锡安。

And he will boast over the people,
而他将在人民面前夸夸其谈。

And he will speak great things in his heart in the presence of the Most High.
他要在至高者的面前，说出他心中的大事。

\Verse        But he also shall fall at last. These are the black waters.
但他最后也要倒下。这些都是黑水。

\Chapter 
\Verse 'And the bright twelfth waters which you have seen: this is the word. 
"你所看见的那明亮的第十二水，就是道。

\Verse For after these things time will come when your people shall fall into distress, so that they shall all run the risk of perishing together. 
因为在这些事之后，你的百姓必有落在苦难中的时候，所以他们都要归于灭亡。

\Verse Nevertheless, they will be saved, and their enemies will fall in their presence. 
然而，他们必得救，他们的敌人也必在他们面前倒下。
\Verse And they will have in (due) time much joy. 
到了那时候，他们将有许多喜乐。
\Verse And at that time after a little interval Zion will again be rebuilt, and its offerings will again be restored, and the priests will return to their ministry, and also the Gentiles will come to glorify it. 
到了那时候，过了一段时间，锡安又要重建，祭品又要恢复，祭司们又要回到他们的事奉上，外邦人也要来荣耀它。
\Verse Nevertheless, not fully as in the beginning. 
然而，还没有完全像开始时那样。
\Verse But it will come to pass after these things that there will be the fall of many nations. 
但在这些事之后，必有许多国家的灭亡。
\Verse These are the bright waters which you have seen.
这些是你们所看见的明水。
\Chapter 
\Verse 'For the last waters which you have seen which were darker than all that were before them, those which were after the twelfth number, which were collected together, belong to the whole world. 
'因为你们所看见的最后的水，比前面的水更暗，那是十二数之后的水，聚集在一起的，是属于全天下的。
\Verse For the Most High made division from the beginning, because He alone knows what will befall. 
因为至高者从一开始就作了分裂，因为只有他自己知道将要发生的事。
\Verse For as to the enormities and the impieties which should be wrought before Him, He foresaw six kinds of them. 
因為至高者在他面前所行的罪惡，他預見了六種。
\Verse And of the good works of the righteous which should be accomplished before Him, He foresaw six kinds of them, beyond those which He should work at the consummation of the age. 
至於義人的善行，在祂面前要成全的，祂預見有六種，超過了在時代結束時要做的
\Verse On his account there were not black waters with black, nor bright with bright; for it is the consummation.
在他的帐中，没有黑的水有黑的，也没有亮的有亮的，因为那是圆满的。

\Chapter 
\Verse 'Hear therefore the interpretation of the last black waters which are to come [after the black]: this the word. 
因此，你要听从最后的黑水的解释：这是道
\Verse Behold! the days come, and it shall be when the time of the age has ripened,
那日子将到，当那时代成熟，

And the harvest of its evil and good seeds has come,
收获所种的或善或恶的果实

That the Mighty One will bring upon the earth and its inhabitants and upon its rulers
全能者将给地球和它的居民以及它的统治者们带来

Perturbation of spirit and stupor of heart.
精神的混乱和心灵的迷惑。

\Verse        And they shall hate one another,
他们将互相憎恨

And provoke one another to fight,
并互相挑衅，互相厮杀。

And the mean shall rule over the honorable,
卑鄙的人将统治着尊贵的人。

And those of low degree shall be extolled above the famous.
而那些低级的人将被赞美，高于著名的人。

\Verse        And the many shall be delivered into the hands of the few,
眾人必被交到少數人手中。

And those who were nothing shall rule over the strong,
而那些原本一无所有的人，将统治强者。

And the poor shall have abundance beyond the rich,
而穷人将拥有超越富人的财富

And the impious shall exalt themselves above the heroic.
虚伪的人要高高在上，英雄的人要高高在上。

\Verse       And the wise shall be silent,
智者将沉默，

And the foolish shall speak,
愚者将说话

Neither shall the thought of men be then confirmed,
人们的想法无从得证

Nor the counsel of the mighty,
虽强者之议也无可奈何

Nor shall the hope of those who hope be confirmed.
希望的人的希望也不会被证实。

\Verse        And when those things which were predicted have come to pass,
而当那些预言中的事情实现了，

Then shall confusion fall upon all men,
然后，混乱将降临到所有人身上。

And some of them shall fall in battle,
他们中的一些人将在战斗中倒下。

And some of them shall perish in anguish,
他们中的一些人将在痛苦中灭亡。

\Verse And some of them shall be destroyed by their own. Then the Most High peoples whom He has prepared before,
他们中的一些人，必被自己所消灭。那时候，至高者所预备的万民,

And they shall come and make war with the leaders that shall then be left.
他们必来与那剩下的领袖开战。

\Verse        And it shall come to pass that whoever gets safe out of the war shall die in the earthquake,
凡从战争中安全地逃出的人，必死在地震中。

And whoever gets safe out of the earthquake shall be burned by the fire,
谁能在地震中安全地逃出来，谁就会被火烧死。

And whoever gets safe out of the fire shall be destroyed by famine.
凡从火中安全地逃出火场的人，必被饥荒所毁灭。


\Verse [And it shall come to pass that whoever of the victors and the vanquished gets safe out of and escapes all these things aforesaid will be delivered into the hands of My servant Messiah.] 
在胜利者和被打败的人中，无论谁能安全地逃出火海，逃过上述的一切事情，就必被送到我的仆人弥赛亚手中。
\Verse For all the earth shall devour its inhabitants.
因为全地的居民必被吞噬。

\Chapter 
\Verse 'And the holy land shall have mercy on its own, And it shall protect its inhabitants at that time. 
圣地必怜悯它自己，在那时候保护它的居民。
\Verse This is the vision which you have seen, and this is the interpretation. 
这是你所看见的异象，这是对你的解释。
\Verse For I have come to tell you these things, because your prayer has been heard with the Most High.
因為我來告訴你們這些事，因為你們的祈求已被至高者聽到了。

\Chapter 
\Verse 'Hear now also regarding the bright lightning which is to come at the consummation after these black (waters): this is the word. 
现在你也要听一听，在这些黑水之后，那将在黑水之后，在大决战时降临的明亮的闪电，就是这句话。
\Verse After the signs have come, of which you were told before, when the nations become turbulent, and the time of My Messiah is come, he shall both summon all the nations, and some of them he shall spare, and some of them he shall slay. 
在眾國動亂，我的彌賽亞的時代來臨之後，他必召喚萬國，有的必赦免，有的必殺害。
\Verse These things therefore shall come upon the nations which are to be spared by Him. 
因此，这些事必临到那些被他赦免的民族身上。
\Verse Every nation, which knows not Israel and has not trodden down the seed of Jacob, shall indeed be spared. 
凡不认识以色列和没有踏过雅各的后裔的民族，都必得饶恕。
\Verse And this because some out of every nation shall be subjected to your people. 
因為每一個民族中，必有一些人受你的子民的影響。
\Verse But all those who have ruled over you, or have known you, shall be given up to the sword.
但所有统治过你的人，或认识你的人，都要被交在刀下。

\Chapter 
\Verse   'And it shall come to pass, when He has brought low everything that is in the world,
当他把世界上的一切都降到最低的时候，它就会到来。

And has sat down in peace for the age on the throne of His kingdom,
并在他的国度的宝座上安详地坐下来，为时代而坐。

That joy shall then be revealed,
这样一来，这种喜悦就会显现出来。

And rest shall appear.
安息将出现。

\Verse        And then healing shall descend in dew,
然后医治将在露水中降临。

And disease shall withdraw,
而疾病也将退出。

And anxiety and anguish and lamentation pass from amongst men,
忧虑、痛苦和哀叹从人中消失。

And gladness proceed through the whole earth.
欢欣鼓舞地传遍全地

\Verse        And no one shall again die untimely,
没有人会再死得不早。

Nor shall any adversity suddenly befall.
任何逆境也不会突然降临。

\Verse        And judgments, and abusive talk, and contentions, and revenges,
审判、辱骂、争吵和报复。

And blood, and passions, and envy, and hatred,
和血，和激情，和嫉妒，和仇恨。

And whatsoever things are like these shall go into condemnation when they are removed.
凡像这样的事，除掉之后，必被定罪。

\Verse        For it is these very things which have filled this world with evils,
因为正是这些东西使这世界充满了罪恶。

And on account of these the life of man has been greatly troubled.
因为这些事物，人类的生活就受到了极大的困扰。

\Verse        And wild beasts shall come from the forest and minister unto men
野兽必从森林里出来，为人作工。

And asps and dragons shall come forth from their holes to submit themselves to a little child.
蟒蛇和龙将从洞里出来，臣服于一个小孩子。

\Verse        And women shall no longer then have pain when they bear,
女人在生孩子的时候就不会再有痛苦。

Nor shall they suffer torment when they yield the fruit of the womb.
他们也不至于在子宫里结出果子的时候受折磨。

\Chapter 
\Verse   'And it shall come to pass in those days that the reapers shall not grow weary,
在那些日子里，收割者必不疲倦。

Nor those that build be toil-worn;
那建造的人，也必疲于奔命。

For the works shall of themselves speedily advance
因为工程本身就必快快进

Together with those who do them in much tranquility.
与那些在宁静中做这些事的人一起。

\Verse        For that time is the consummation of that which is corruptible,
因为时间是对那些腐朽的东西的消耗。

And the beginning of that which is not corruptible.
而那不朽坏的事物的开始。

\Verse        Therefore those things which were predicted shall belong to it:
所以那些被预言的东西，必属于它。

Therefore it is far away from evils, and near to those things which die not.
所以它远离罪恶，靠近那些不死之物。

\Verse        This is the bright lightning which came after the last dark waters.'
这是在最后黑暗的水之后的明亮的闪电。

\par
75. Baruch's Hymn on the Unsearchableness of God's Ways and on His Mercies  through which the Faithful shall attain to a blessed Consummation
\par
75. 巴录的赞美诗："神的道路是不可寻觅的，他的恩典是信士们将通过他的恩典达到有福的圆满"。
\par
\Chapter 
\Verse   And I answered and said:
我回答说："

'Who can understand, O Lord, Your goodness
主啊，你的仁慈，誰能明白呢？

For it is incomprehensible.
因为它是不可理解的。

\Verse        Or who can search into your compassions,
谁能懂你的爱人之心

Which are infinite
那无尽的同情

\Verse        Or who can comprehend Your intelligence
谁人能理解你的智慧

\Verse        Or who is able to recount the thoughts of Your mind
能计数你心中的想法

\Verse        Or who of those who are born can hope to come to those things,
或者说，谁的生而为人，谁就能希望来到那些事。

Unless he is one to whom you are merciful and gracious
除非你对他是个仁慈和仁慈的人。

\Verse        Because, if assuredly you did not have compassion on man,
因为，如果你没有对人有怜悯之心，就不会有怜悯之心。

Those who are under Your right hand,
那些在你的右手下的人。

They could not come to those things,
他们不可能来找这些事情。

But those who are in the numbers named can be called.
但那些在被命名的数字中的人可以被称为。

\Verse        But if, indeed, we who exist know wherefore we have come,
但是，如果我们存在的人知道我们来的原因。

And submit ourselves to Him who brought us out of Egypt,
把自己交给把我们带出埃及的神。

We shall come again and remember those things which have passed,
我们会再来，记住那些已经过去的事情。

And shall rejoice regarding that which has been.
我必为过去的事而欢欣鼓舞。

\Verse        But if now we know not wherefore we have come,
但是，如果我們現在不知道我們為什麼而來，我們就不知道。

And recognize not the principate of Him who brought us up out of Egypt, We shall come again and seek after those things which have been now,
直到若不是他带我们出了埃及，？？？？。

And be grieved with pain because of those things which have befallen.'
并为这些事情的发生而悲痛不已。
\par
76. Baruch bidden to instruct the People for forty days and then to hold himself ready for his Assumption on the Advent of the Messiah
\par
76. 巴录受命指示百姓四十天，然后在弥赛亚降临之时，准备好了自己的受托仪式。
\par
\Chapter 
\Verse And He answered and said unto me: ['Inasmuch as the revelation of this vision has been interpreted to you as you requested], hear the word of the Most High that you may know what is to befall you after these things.
他回答我说，如你所求，你要的异象已经为你解释。
聆听至高神的话语，你便知道那些事之后你将面临的事情。
\Verse For you shall surely depart from this earth, nevertheless not unto death, but you shall be preserved unto the consummation of the times. 
因為你們必從地上離開，但不至於死，但你們必得保全，直到時代的結束。
\Verse Go up therefore to the top of that mountain, and there shall pass before you all the regions of that land, and the figure of the inhabited world, and the top(s) of the mountains, and the depth(s) of the valleys, and the depths of the seas, and the number of the rivers, that you may see what you are leaving, and whither you are going. 
你们要上到那山顶上，那地的一切区域，那地的形状，山的顶，谷的深浅，海的深浅，河的深浅，河的数目，都要在你们面前经过，叫你们看清你们要离开的是什么，要往哪里去。
\Verse Now this shall befall after forty days. Go now therefore during these days and instruct the people so far as you are able, that they may learn so as not to die at the last time, but may learn in order that they may live at the last times.'
這事必在四十天後發生。你要在这些日子里，尽你的能力去教导百姓，使他们学习，免得在最后的时候死掉，但要学习，使他们在最后的时候活下来。
\par
77. Baruch's Admonition to the People and his writing of two Letters—one to the nine and a half tribes in Assyria and the other to the two and a half in Babylon
\par
77. 巴录对人民的训诫和他写的两封信----写给亚述的九个半部族和巴比伦的两个半部族。
\par
\Chapter 
\Verse And I, Baruch, went there and came to the people, and assembled them together from the greatest to the least, and said unto them: 
我巴录就到那里去，到百姓那里去，把他们从大到小聚集在一起，对他们说："你们听啊！"我说：
\Verse 'Hear, you children of Israel, behold how many you are who remain of the twelve tribes of Israel. 
你们以色列的子民啊，你们要听着，看哪，以色列十二支派中还有多少人。
\Verse For to you and to your fathers the Lord gave a law more excellent than to all peoples. 
因為耶和華賜給你們和你們的祖宗的律法，比賜給萬民的律法更優勝。
\Verse And because your brethren transgressed the commandments of the Most High,
因為你們的弟兄們違背了至高者的誡命。

He brought vengeance upon you and upon them,
他给你和他们报了仇。

And He spared not the former,
而他也不放过前者。

And the latter also He gave into captivity:
后者也被他俘虏了。

And He left not a residue of them,
祂也不留任何残余的东西。

\Verse        But behold! you are here with me.
但看哪，你在这里和我在一起。

\Verse        If, therefore, you direct your ways aright,
因此，如果，你的方法是正确的。

Ye also shall not depart as your brethren departed,
你们也不可像你们的弟兄们离去时那样离去。

But they shall come to you.
但他们必来找你们。

\Verse        For He is merciful whom you worship,
因为你们敬拜的人是仁慈的。

And He is gracious in whom you hope,
而他是你所希望的恩人。

And He is true, so that He shall do good and not evil.
祂是真的，所以祂必行善，不作恶。

\Verse        Have you not seen here what has befallen Zion
你们难道没有看到锡安所遭遇的事吗？

\Verse        Or do you perchance think that the place had sinned,
或者你是否认为这个地方犯了罪。

And that on this account it was overthrown
就因为这个原因，它被推翻了。

Or that the land had wrought foolishness,
或者说，这块土地上的人犯了傻。

And that therefore it was delivered up
因此，它被送了上来


\Verse      And know you not that on account of you who did sin,
而且知道你不知道，因为你的罪过。

That which sinned not was overthrown,
没有罪过的人被推翻了。

And, on account of those who wrought wickedly,
而且，因为那些作恶多端的人。

That which wrought not foolishness was delivered up to (its) enemies'
那不是愚昧的人，被送到了敌人的面前。

\Verse And the whole people answered and said unto me: 'So far as we can recall the good things which the Mighty One has done unto us, we do recall them; and those things which we do not remember He in His mercy knows. 
众人回答说：'只要我们能记起全能者对我们所行的善事，我们就记起，那些我们不记起的事，他在他的怜悯中也知道。
\Verse Nevertheless, do this for us your people: write also to our brethren in Babylon an epistle of doctrine and a scroll of hope, that you may confirm them also before you do depart from us.
然而，你們要為我們你們的子民作這樣的事，也要為我們巴比倫的弟兄們寫一封教義的書信和一卷希望的書信給我們的弟兄們，求你們在離開我們之前，也要確立他們。

\Verse      For the shepherds of Israel have perished,
因为以色列的牧羊人已经灭亡了。

And the lamps which gave light are extinguished,
而那些给光的灯也熄灭了。

And the fountains have withheld their stream whence we used to drink.
泉眼已经停止了我们曾经喝过的水。

\Verse      And we are left in the darkness,
我们被留在了黑暗中。

And amid the trees of the forest,
而在森林中的树木中。

And the thirst of the wilderness.'
和旷野的干渴。

\Verse      And I answered and said unto them
我回答他们说

'Shepherds and lamps and fountains come from the law:
牧羊人和灯和喷泉都来自于律法。

And though we depart, yet the law abides.
我们虽然离去，但律法仍在。

\Verse      If therefore you have respect to the law,
如果你们尊重律法

And are intent upon wisdom,
并立志于智慧。

A lamp will not be wanting,
一盏台灯就不会要了。

And a shepherd will not fail,
牧羊人也不会失败。

And a fountain will not dry up.
而喷泉也不会干涸。

\Verse Nevertheless, as you said unto me, I will write also unto your brethren in Babylon, and I will send by means of men, and I will write in like manner to the nine tribes and a half, and send by means of a bird.' 
你对我说过，我也要写信给你在巴比伦的弟兄们，我也要用人送去，我也要用同样的方法写信给九支派半的人，用鸟送去。
\Verse And it came to pass on the one and twentieth day in the eighth month that I, Baruch, came and sat down under the oak under the shadow of the branches, and no man was with me, but I was alone. 
到了第八个月的一天二十日，我巴录来了，坐在橡树下，在树枝的阴影下，没有人和我在一起，只有我一个人。
\Verse And I wrote these two epistles: one I sent by an eagle to the nine and a half tribes; and the other I sent to those that were at Babylon by means of three men. 
我就写了这两封书信，一封是我借着鹰寄给九个半支派的人，另一封是我借着三个人寄给巴比伦的人。
\Verse And I called the eagle and spoke these words unto it: 
我叫那鹰，对它说了这些话。
\Verse 'The Most High hath made you that you should be higher than all birds. 
至高者所造你們，使你們高於眾鳥。
\Verse And now go and tarry not in (any) place, nor enter a nest, nor settle upon any tree, till you have passed over the breadth of the many waters of the river Euphrates, and have gone to the people that dwell there, and cast down to them this epistle. 
现在你们要去，不要在任何地方逗留，也不要进巢，也不要在树上住下，直到你们过了幼发拉底河的许多水面，到那里的人那里去，把这书信丢给他们。
\Verse Remember, moreover, that, at the time of the deluge, Noah received from a dove the fruit of the olive, when he sent it forth from the ark. 
还记得，在大洪水的时候，挪亚从方舟上送出橄榄果子的时候，从鸽子那里得到了橄榄果子。
\Verse Yea, also the ravens ministered to Elijah, bearing him food, as they had been commanded. 
是的，乌鸦也向以利亚献祭，给他带食物，正如他们所吩咐的那样。
\Verse Solomon also, in the time of his kingdom, whithersoever he wished to send or seek for anything, commanded a bird (to go thither), and it obeyed him as he commanded it. 
所罗门也在他的国度里，无论他想打发或寻找什么，就吩咐一只鸟去那里，它就听从他的吩咐。
\Verse And now let it not weary you, and turn not to the right hand nor the left, but fly and go by a direct way, that you may preserve the command of the Mighty One, according as I said unto you.'
現在，你們不要使它疲倦，也不要向右轉，也不要向左轉，而要直接飛去，按我對你們所說的話，你們可以遵守全能者的命令。
\par
78—86. THE EPISTLE OF BARUCH THE SON OF NERIAH WHICH HE WROTE TO THE NINE AND A HALF TRIBES
\par
78—86. 尼雅之子巴录写给九支半部落的书信
\par
\Chapter 
\Verse These are the words of that epistle which Baruch the son of Neriah sent to the nine and a half tribes, which were across the river Euphrates, in which these things were written.
这些是尼雅的儿子巴录寄给幼发拉底河对岸的九个半部落的书信中写的。

\Verse Thus says Baruch the son of Neriah to the brethren carried into captivity: 'Mercy and peace.' I bear in mind, my brethren, the love of Him who created us, who loved us from of old, and never hated us, but above all educated us. 
尼雅的儿子巴鲁对被掳的弟兄们说："怜悯与平安。我的弟兄们，我谨记着创造我们的人的爱，他从古以来爱我们，不曾憎恨我们，但最重要的是教育我们。
\Verse And truly I know that behold all we the twelve tribes are bound by one bond, inasmuch as we are born from one father. 
我知道我们十二个支派的人都有一个纽带，因为我们都是从一个父亲出生的。
\Verse Wherefore I have been the more careful to leave you the words of this epistle before I die, that you may be comforted regarding the evils which have come upon you, and that you may be grieved also regarding the evil that has befallen your brethren; and again, also, that you may justify His judgment which 
所以我在我死之前，就更小心地把这书信的话留给你们，叫你们因着临到你们身上的罪恶得到安慰，也叫你们因着你们的弟兄所受的祸害而忧愁，也叫你们因着他的审判而称义。
\Verse He has decreed against you that you should be carried away captive—for what you have suffered is disproportioned to what you have done—in order that, at the last times, you may be found worthy of your fathers. 
我已命令你們，要把你們帶走，因為你們所受的苦，與你們所做的事不相稱，以便在最後的時候，你們能被發現配得上你們的祖宗。
\Verse Therefore, if you consider that ye have now suffered those things for your good, that you may not finally be condemned and tormented, then you will receive eternal hope; if above all you destroy from your heart vain error, on account of which you departed hence. 
所以，你们若认为你们现在受了这些事是为你们好，免得最后被定罪受苦，受了折磨，就必得永生的盼望。
\Verse For if you so do these things, He will continually remember you, He who always promised on our behalf to those who were more excellent than we, that He will never forget or forsake us, but with much mercy will gather together again those who were dispersed.
因為你若這樣行這些事，祂必永遠記念你們，那常為我們應許給比我們更優秀的人的人，祂永遠不會忘記我們，也不會拋棄我們，必以大慈大悲把那些被拋棄的人聚集起來。

\Chapter 
\Verse Now, my brethren, learn first what befell Zion: how that Nebuchadnezzar king of Babylon came up against us. 
我的弟兄们，你们要先知道锡安的遭遇，巴比伦的尼布甲尼撒王是怎样对付我们的。
\Verse For we have sinned against Him who made us, and we have not kept the commandments which he commanded us, yet he hath not chastened us as we deserved. 
因为我们得罪了造我们的主，我们没有遵守他所吩咐我们的诫命，他却没有按着我们所应得的惩罚我们。
\Verse For what befell you we also suffer in a preeminent degree, for it befell us also.
因为你们所受的，我们也在很大程度上受了苦，因为我们也受了苦。

\Chapter 
\Verse And now, my brethren, I make known unto you that when the enemy had surrounded the city, the angels of the Most High were sent, and they overthrew the fortifications of the strong wall, and they destroyed the firm iron corners, which could not be rooted out. 
我的弟兄们，现在我告诉你们，当敌人包围了城，至高者的天使被差遣来了，他们推翻了坚固的城墙，摧毁了坚固的铁角，使之无法根除。
\Verse Nevertheless, they hid all the vessels of the sanctuary, lest the enemy should get possession of them. 然而，他们把圣所的器皿都藏起来，免得仇敌夺取。
\Verse And when they had done these things, they delivered thereupon to the enemy the overthrown wall, and the plundered house, and the burnt temple, and the people who were overcome because they were delivered up, lest the enemy should boast and say: 他们做了这些事，就把那被推翻的墙，被掠夺的房子，被烧毁的殿，和因被送上来而得胜的百姓，都交给仇敌，免得仇敌夸口说。
\Verse'Thus by force have we been able to lay waste even the house of the Most High in war.' Your brethren also have they bound and led away to Babylon, and have caused them to dwell there. "我们就这样用武力，连至高者的家也在战争中被毁坏了。你们的弟兄们也被捆绑着带去巴比伦，使他们住在那里。
\Verse But we have been left here, being very few. 但我们却被留在这里，人数很少。
\Verse This is the tribulation about which I wrote to you. 這就是我寫給你們的災難。
\Verse For assuredly I know that (the consolation of) the inhabitants of Zion consoles you : so far as you knew that it was prospered (your consolation) was greater than the tribulation which you endured in having to depart from it.
因为我实在知道锡安居民的安慰安慰你们：只要你们知道锡安是繁荣的，你们的安慰就比你们不得不离开锡安所受的磨难还要大。
\Chapter 
\Verse But regarding consolation, hear the word. 但关于安慰，你要听话。
\Verse For I was mourning regarding Zion, and I prayed for mercy from the Most High, and I said:
因为我为锡安哀悼，求至高者的怜悯，我说：

\Verse        'How long will these things endure for us
这些东西会给我们带来多长时间？

And will these evils come upon us always'
而这些罪恶会不会永远降临到我们身上？

\Verse        And the Mighty One did according to the multitude of His mercies,
全能者按他的恩惠的眾多而做了。

And the Most High according to the greatness of His compassion,
至高者按着他的大慈大悲的大慈大悲。

And He revealed unto me the word, that I might receive consolation,
他向我启示了话语，使我可以得到安慰。

And He showed me visions that I should not again endure anguish,
祂向我显出异象，叫我不要再忍受痛苦。

And He made known to me the mystery of the times.
他让我知道了时代的奥秘。

And the advent of the hours he showed me.
他向我显明了时间的来临。

\Chapter 
\Verse Therefore, my brethren, I have written to you, that you may comfort yourselves regarding the multitude of your tribulations. 
所以，我的弟兄们，我写信给你们，叫你们在你们的苦难中得到安慰。
\Verse For know you that our Maker will assuredly avenge us on all our enemies, according to all that they have done to us, also that the consummation which the Most High will make is very nigh, and His mercy that is coming, and the consummation of His judgment, is by no means far off.
因为你们知道，我们的造物主必按着他们对我们所行的一切，向我们的仇敌报仇，至高者所行的大限已近，他的怜悯和审判的大限也不远了。

\Verse        For lo! we see now the multitude of the prosperity of the Gentiles,
因為我們現在看見外邦人的興旺，是眾多的。

Though they act impiously,
虽然他们的行为很粗鲁。

But they shall be like a vapor:
但是，他们应像蒸气一样。

\Verse        And we behold the multitude of their power,
而我们看到了他们的众多力量。

Though they do wickedly,
虽然他们做得很邪恶。

But they shall be made like unto a drop:
但他们要像一滴水一样.

\Verse        And we see the firmness of their might.
我们看到了他们的力量的坚固。

Though they resist the Mighty One every hour,
虽然他们每时每刻都在抵抗大能者

But they shall be accounted as spittle.
但他们将被算作唾沫。

\Verse        And we consider the glory of their greatness,
我们考虑他们的伟大的荣耀。

Though they do not keep the statutes of the Most High,
虽然他们不遵守至高者的章程。

But as smoke shall they pass away.
但如烟消云散

\Verse        And we meditate on the beauty of their gracefulness,
我们沉思着他们的优雅之美。

Though they have to do with pollutions,
尽管它们与污染有关。

But as grass that withers shall they fade away.
但就像枯萎的草一样，它们也会凋零。

\Verse        And we consider the strength of their cruelty,
而我们考虑的是他们的残酷性的力量。

Though they remember not the end (thereof),
虽然他们不记得结局（其）。

But as a wave that passes shall they be broken.
但是，他们必被打碎。

\Verse        And we remark the boastfulness of their might,
我们说他们的力量太过夸耀了。

Though they deny the beneficence of God, who gave (it) to them,
虽然他们否认上帝的恩惠，因为上帝给了他们

But they shall pass away as a passing cloud.
但他们必如过眼云烟般消逝。

\Chapter 
\Verse   [For the Most High will assuredly hasten His times,
因为至高者必使他的时代更快。

And He will assuredly bring on His hours.
祂必確實帶來祂的時間。

\Verse        And He will assuredly judge those who are in His world,
祂必定然审判那些在祂世界里的人。

And will visit in truth all things by means of all their hidden works.
他必以真理探访万物，借着他们一切隐秘的功课。

\Verse        And He will assuredly examine the secret thoughts,
他確已察覺到他們的秘密思想。

And that which is laid up in the secret chambers of all the members of mail. And will make (them) manifest in the presence of all with reproof.
而那些在密室里的所有成员的密室里的东西。我必使他们在众人面前显露出来，以责备他们。

\Verse Let none therefore of these present things ascend into your hearts, but above all let us be expectant, because that which is promised to us shall come. 
因此，你們不要把這些事放在心裡，但最重要的是，我們要盼望，因為那應許我們的事必來。
\Verse And let us not now look unto the delights of the Gentiles in the present, but let us remember what has been promised to us in the end. 
我們現在不要看外邦人現在的喜悅，但要記住所應許給我們的事。
\Verse For the ends of the times and of the seasons and whatsoever is with them shall assuredly pass by together. 
时代的尽头，季节的尽头，以及与之同在的一切，都必一同过去。
\Verse The consummation, moreover, of the age shall then show the great might of its ruler, when all things come to judgment. 
而且，当万事都要受审判的时候，时代的终结将显示出统治者的大能。
\Verse Do you therefore prepare your hearts for that which before you believed, lest you come to be in bondage in both worlds, so that you be led away captive here and be tormented there. 
所以你们要为你们之前所信的事预备好心，免得你们在这两个世界中被捆绑，在这里被掳走，在那里受苦。
\Verse For that which exists now or which has passed away, or which is to come, in all these things, neither is the evil fully evil, nor again the good fully good.
因為那現在存在的、已經過去的、或將要來的，在這一切的事上，既不是完全的惡，也不是完全的善。

\Verse      For all healthinesses of this time are turning into diseases,
因为这个时代所有的健康都会变成疾病。

\Verse      And all might of this time is turning into weakness,
而这个时候所有的力量都变成了软弱。

And all the force of this time is turning into impotence,
而这个时候所有的力量都变成了无能。

\Verse      And every energy of youth is turning into old age and consummation.
而每一个青春的能量都在化作老去的岁月和消耗。

And every beauty of gracefulness of this time is turning faded and hateful,
而这个时代的每一种优雅的美，都在变淡，变的可恨。

\Verse      And every proud dominion of the present is turning into humiliation and shame,
而现在的每一个骄傲的主宰都变成了羞辱和耻辱。

\Verse      And every praise of the glory of this time is turning into the shame of silence,
而这时代的荣耀的每一次赞美都变成了沉默的耻辱。

And every vain splendor and insolence of this time is turning into voiceless ruin.
而这个时代的每一个虚妄的辉煌和傲慢都在变成无声的毁灭。

\Verse      And every delight and joy of this time is turning to worms and corruption,
而这个时代的每一个快乐和喜悦，都变成了虫子和腐败。

\Verse      And every clamor of the pride of this time is turning into dust and stillness.
而这个时代的每一个骄傲的喧嚣，都在化为尘埃和寂静。

\Verse      And every possession of riches of this time is being turned into Sheol alone,
而这时代的每一个财富的拥有者，都被单独地变成了地狱。

\Verse      And all the rapine of passion of this time is turning into involuntary death,
而这个时代所有的激情强奸，都变成了无意识的死亡。

And every passion of the lusts of this time is turning into a judgment of torment.
而这个时代的每一个情欲的激情都变成了审判的折磨。

\Verse      And every artifice and craftiness of this time is turning into a proof of the truth,
这时代的每一个诡计和狡诈都变成了真理的证明。

\Verse      And every sweetness of unguents of this time is turning into judgment and condemnation,
而这时代的每一个甜头都变成了审判和谴责。

\Verse      And every love of lying is turning to contumely through truth.
而每一个爱说谎的人，都会因真理而转而为谎言。

\Verse [Since therefore all these things are done now, does anyone think that they will not be avenged But the consummation of all things will come to the truth.]
既然这一切的事都已经做了，有人认为他们不会被报复吗？

\Chapter 
\Verse Behold! I have therefore made known unto you (these things) whilst I live: for I have said (it) that you should learn the things that are excellent; for the Mighty One hath commanded me to instruct you: and I will set before you some of the commandments of His judgment before I die. 
看哪，看哪，看哪，看哪。在我活著的時候，我確已將這些事告訴你們，因為我說：「你們應當學習至善的事，因為全能者曾吩咐我指示你們，在我死前，我將把他的一些誡命放在你們面前。
\Verse Remember that formerly Moses assuredly called heaven and earth to witness against you and said: 'If you transgress the law you shall be dispersed, but if you keep it you shall be kept.' 
记得以前摩西曾叫天地见证你们，说："你们若违犯律法，必被驱散；若遵守律法，必被保守。
\Verse And other things also he used to say unto you when you the twelve tribes were together in the desert. 
他还对你们十二支派在沙漠中的时候，也曾对你们说过其他的事。
\Verse And after his death you cast them away from you: on this account there came upon you what had been predicted. 
他死后，你们就把他们赶走了，如同预言所说。
\Verse And now Moses used to tell you before they befell you, and lo! they have befallen you: for you have forsaken the law. 
摩西以前曾告訴你們，在他們臨到你們之前，他們已經臨到了你們，因為你們背棄了律法。
\Verse Lo! I also say unto you after you have suffered, that if you obey those things which have been said unto you, you will receive from the Mighty One whatever has been laid up and reserved for you. 
我也告訴你們，你們受苦之後，我又對你們說，你們若遵從對你們所說的事，就必從全能者那裡得到所立的和為你們預備的一切。
\Verse Moreover, let this epistle be for a testimony between me and you, that you may remember the commandments of the Mighty One, and that also there may be to me a defense in the presence of Him who sent me. 
而且，这书信是我和你们之间的见证，使你们可以记住全能者的诫命，也可以在差我来的人面前为我辩护。
\Verse And remember you the law and Zion, and the holy land and your brethren, and the covenant of your fathers, and forget not the festivals and the Sabbaths. 
你们要记住律法和锡安，圣地和你们的弟兄们，以及你们列祖的约，不要忘记节日和安息日。
\Verse And deliver this epistle and the traditions of the law to your sons after you, as also your fathers delivered (them) to you. 
要把这书信和律法的传统传给你们的儿子，如同你们的祖宗传给你们一样。
\Verse And at all times make request perseveringly and pray diligently with your whole heart that the Mighty One may be reconciled to you, and that He may not reckon the multitude of your sins, but remember the rectitude of your fathers. 
你們要時刻懇切地祈求，全心全意地禱告，求全能者與你們和好，求他不計較你們的罪過，只記念你們祖宗的正直。
\Verse For if He judge us not according to the multitude of His mercies, woe unto all us who are born.
因为如果他不按他的恩典的多寡来审判我们，那我们所有生来的人就有祸了。
\Chapter 
\Verse   [Know, moreover, that
[此外，还要知道，

In former times and in the generations of old our fathers had helpers, 
在从前，在我们的父辈中，我们的父辈都有帮手。

Righteous men and holy prophets:
正义的人和圣洁的先知。

\Verse        No more, we were in our own land
我们已经不再我们自己的土地上

[And they helped us when we sinned].
[他们在我们犯罪时帮助了我们]。

